---
title: "01_Test_pie_maps"
output: html_document
---

Testing some approaches for putting pies on maps   

## 0. Libs + map
```{r}
library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(readxl)
map_norway <- map_data("world", "Norway")
map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()

```

## 1. Plot just a map (with a point)
```{r}
df <- data.frame(long = 10.66, lat = 59.92)
gg <- ggplot(df, aes(long, lat)) +
    annotation_map(map_norway, fill = "grey60") +
  geom_point() +
  coord_map("lambert", parameters = c(64, 12), xlim = c(-1,30), ylim = c(57, 72))
gg
```
### b. Manual transformation 
```{r}

proj_name <- "lambert"
proj_par = c(64, 12)

xtabs(~subregion, map_norway)
map_norway <- subset(map_norway, !subregion %in% c("Svalbard", "Jan Mayen"))

projlist <- with(map_norway, mapproject(long, lat, proj_name, parameters = proj_par))
map_norway2 <- map_norway
map_norway2[["long"]] <- projlist[["x"]]
map_norway2[["lat"]] <- projlist[["y"]]
            
# range(projlist[["y"]])

# Entire map
# df <- data.frame(long = projlist[["range"]][1:2], lat = projlist[["range"]][3:4])

# Self-set lim

df <- data.frame(long = c(5, 31, 10.66), lat = c(58, 71, 59.92))
# X <- mapproject(df$long, df$lat, proj_name, parameters = proj_par)  # Doesn't work; orientation differs  
X <- mapproject(df$long, df$lat)                                      # Does work; uses previous orientation
df_proj <- data.frame(long = X$x, lat = X$y )
gg <- ggplot(df_proj, aes(long, lat)) +
    annotation_map(map_norway2, fill = "grey60") +
  geom_point() +
  coord_cartesian(xlim = c(-0.10, 0.075))
gg

```

## 2. Package 'gridGraphics'  
### a. Example  
```{r}
data.frame(x = 2:10, y = 12:20) -> dat
plot(dat$x, dat$y)
pie(rep(1,5), col = rainbow(5), labels = NA, radius = 1)
grid.echo()
grid.grab() -> mapgrob
ggplot(data = dat) + geom_point(aes(x = x, y = y)) 
pushViewport(viewport(x = .8, y = .4, height = .2, width = .2))    
grid.draw(mapgrob)
```

### b. On a map   
Note tha coordinates are (0,1) for both x and y, unrelated relative to plot
```{r}
pie(rep(1,6), col = rainbow(6), labels = NA, radius = 1)
grid.echo()
grid.grab() -> mapgrob
gg
pushViewport(viewport(x = .5, y = .5, height = .2, width = .2))    
grid.draw(mapgrob)
```

## 3. Package 'ggimage'  
### a. Example from vignette  
[Link](https://cran.r-project.org/web/packages/ggimage/vignettes/ggimage.html#geom_icon)   
```{r}
# install.packages("ggimage")
library(ggimage)

# library(tibble)
dd <- data.frame(x=LETTERS[1:3], y=1:3)
pie <- ggplot(dd, aes(x=1, y, fill=x)) + geom_bar(stat="identity", width=1) + coord_polar(theta="y") +
    theme_void() + theme(legend.position="none") + theme_transparent()

df <- data_frame(x = sample(2:9),
                 y = sample(2:9),
                 width = sample(seq(0.5, 3, length.out=length(x))),
                 pie = list(pie))
p <- ggplot(data=data.frame(x=c(0, 10), y=c(0, 10)), aes(x, y))+geom_blank()
p + geom_subview(aes(x=x, y=y, subview=pie, width=width, height=width), data=df)
```

### b. Based on vignette example: plotting different pies
```{r}
# library(tibble)
dd <- data.frame(Type = rep(1:2, each = 3), 
                 x = rep(c("purple", "pink", "brown"), 2), 
                 y = c(1:3, 2,2,2))
pie <- ggplot(dd %>% filter(Type == 2), aes(x=1, y, fill=x)) + geom_bar(stat="identity", width=1) + coord_polar(theta="y") +
    theme_void() + theme(legend.position="none") + theme_transparent()
pie

pietypes <- unique(dd$Type)
n_pietypes <- length(pietypes)
pie_list <- vector("list", n_pietypes)
for (i in 1:n_pietypes){
  pietype <- pietypes[i]
  pie_list[[i]] <- ggplot(subset(dd, Type %in% pietype), aes(x=1, y, fill=x)) + 
    geom_bar(stat="identity", width=1) + 
    scale_fill_manual(values = c("firebrick4", "darkorchid2", "violet")) + 
    coord_polar(theta="y") +
    theme_void() + theme(legend.position="none") + theme_transparent()
}

df <- data_frame(x = 1:2,
                 y = 1:2,
                 width = rep(1,2),
                 pie = pie_list
)
p <- ggplot(data=data.frame(x=c(0, 4), y=c(0, 4)), aes(x, y))+geom_blank()
p + geom_subview(aes(x=x, y=y, subview=pie, width=width, height=width), data=df)
```

### c. Put on a map 
```{r}
df <- data_frame(x = c(7, 11),
                 y = c(59, 61),
                 width = rep(1.5,2),
                 pie = pie_list
)
p <- ggplot(data=data.frame(x = c(-1,36), y = c(58.5, 72)), aes(x, y)) + 
  geom_blank() +
  annotation_map(map_norway, fill = "grey60") +
  geom_subview(aes(x=x, y=y, subview=pie, width=width, height=width), data=df)
p

# p + coord_map("lambert", parameters = c(64, 12), xlim = c(-1,30), ylim = c(57, 72))
# Error: annotation_custom only works with Cartesian coordinates

```

## 4. Data
### a. Read data
```{r}
library(sp)        # SpatialPoints(), CRS(), spTransform()

df_stations <- read_excel("Data_input/StasonsOgPrøvetakingsoversiktElveovervåking_30_10.xlsx")
```


### b. Functions for converting from UTM to long/lat  
```{r}
# Converts utm to long-lat and (if return_entire_dataframe = TRUE) adds the variables to the data frame
# For one single UTM zone
utm2longlat_onezone <- function(df, xvar = "x", yvar = "y", zone, return_entire_dataframe = FALSE){
  crs_utm <- paste0("+proj=utm +zone=", zone, " +ellps=WGS84 +datum=WGS84 +units=m")
  SP.utm <- SpatialPoints(df[,c(xvar, yvar)], 
                          proj4string=CRS(crs_utm)
                          )
  SP.longlat <- spTransform(SP.utm, CRS("+proj=longlat"))
  if (!return_entire_dataframe){
    df <- data.frame(Long = SP.longlat@coords[,1], Lat = SP.longlat@coords[,2])
  } else {
    df$Long <- SP.longlat@coords[,1]
    df$Lat <- SP.longlat@coords[,2]
  }
  df
}

# utm2longlat_onezone(df_stations[1:10, ], "X-koordinat", "Y-koordinat", zone = 32)

# As 'utm2longlat_onezone', but also picks data for that zone (used in 'utm2longlat')
utm2longlat_onezone2 <- function(df, zonevar, zone, ...){
  df2 <- df[df[[zonevar]] %in% zone,]
  utm2longlat_onezone(df2, zone = zone, ...)
  }

# utm2longlat_onezone2(df_stations[38:42, ], "Sone", zone = 32, xvar = "X-koordinat", yvar = "Y-koordinat")

# Converts utm to long-lat and (if return_entire_dataframe = TRUE) adds the variables to the data frame
# UTM zone given as a variable in the data 
# Note: the order the of output data is shuffled 
utm2longlat <- function(df, xvar = "x", yvar = "y", zonevar = "zone", return_entire_dataframe = FALSE){
  zones <- unique(df[[zonevar]])
  df <-   
    purrr::map_df(zones, ~utm2longlat_onezone2(df, zonevar = zonevar, zone = ., xvar = xvar, yvar = yvar, 
                                        return_entire_dataframe = return_entire_dataframe)
    )
  df
}

# df_stations[38:42, "Sone"]
# utm2longlat(df_stations[38:42, ], "X-koordinat", "Y-koordinat", "Sone")
# utm2longlat(df_stations[38:42, ], "X-koordinat", "Y-koordinat", "Sone", return_entire_dataframe = TRUE)

```

### c. Convert UTM to Lang/Lot 
```{r}
df_stations <- utm2longlat(df_stations, "X-koordinat", "Y-koordinat", "Sone", 
                           return_entire_dataframe = TRUE) %>%
  arrange(Rapportnavn)
```

### d. Test map
```{r}
df <- data.frame(long = 10.66, lat = 59.92)
gg <- ggplot(df_stations, aes(Long, Lat)) +
    annotation_map(map_norway, aes(long, lat), fill = "grey60") +
  geom_point() +
  geom_point(data = df_stations %>% filter(Long > 7 & Lat < 61), color = "red")+
  geom_point(data = df_stations %>% filter(Long < 7 & Lat < 63), color = "blue") +
  geom_point(data = df_stations %>% filter(Long > 16 & Lat > 68), color = "green") +
  coord_map("lambert", parameters = c(64, 12), xlim = c(-1,30), ylim = c(57, 72))
gg

```

## 5. Use real data
### a. Test making pie  
Example: missing Fisk (pie piece no. 1)
```{r}

# colnames(df_stations) %>% dput()
vars <- c("Fisk", "Bunndyr", "Begroingsalger", "Fysisk-kjemiske kvalitets elementer", 
          "Vannregion spesifikke stoffer", "Prioriterte stoffer")
cols <- c("darkorchid2", "darkorchid3", "darkorchid4", "brown2", "brown3", "brown4")
sel_lacking <- is.na(df_stations[1, vars])
#  Fisk Bunndyr Begroingsalger Fysisk-kjemiske kvalitets elementer Vannregion spesifikke stoffer
#  TRUE   FALSE          FALSE                               FALSE                         FALSE
#  Prioriterte stoffer
#                FALSE
cols[sel_lacking] <- "grey70"
pie_data <- data.frame(x = 1, y = rep(1,6), label = vars)
pie <- ggplot(pie_data, aes(x=x, y, fill=label)) + 
  geom_bar(stat="identity", width=1) + coord_polar(theta="y") +
  scale_fill_manual(values = cols) +
  theme_void() + theme(legend.position="none") + theme_transparent()
pie
```


### b. Function
```{r}
vars <- c("Fisk", "Bunndyr", "Begroingsalger", "Fysisk-kjemiske kvalitets elementer", 
          "Vannregion spesifikke stoffer", "Prioriterte stoffer")
colorscheme1 <- c("darkorchid2", "darkorchid3", "darkorchid4", "brown2", "brown3", "brown4")

make_pie <- function(measurements_present, col = colorscheme1, col_lacking = "grey80"){
  col[!measurements_present] <- col_lacking
  pie_data <- data.frame(x = vars, y = rep(1,6))
  ggplot(pie_data, aes(x=1, y, fill=x)) + 
    geom_bar(stat="identity", width=1) + coord_polar(theta="y") +
    scale_fill_manual(values = col) +
    theme_void() + theme(legend.position="none") + theme_transparent()
  }

# make_pie(c(TRUE, TRUE, FALSE, TRUE, FALSE, TRUE))
# make_pie(rep(TRUE, 6))
```


### c. Define pies from real data
```{r, fig.height=11}
make_pie_linenumber <- function(i)
  make_pie(!is.na(df_stations[i, vars]))
# make_pie_linenumber(1)
# make_pie_linenumber(20)

pies <- 1:nrow(df_stations) %>% purrr::map(~make_pie_linenumber(.))
length(pies)
# pies[[20]]

df_pies <- data_frame(x = df_stations[["Long"]],
                 y = df_stations[["Lat"]],
                 label = df_stations[["Rapportnavn"]],
                 pie = pies
)
# df[2,]$pie
```

### d. Map, all of Norway
```{r, fig.height=11}
# Define two points in lower left and upper right corner (just used to set the drawing canvas)
df_range <- data.frame(x = c(5.72, 31), y = c(58.14, 71))

df_pies$width = 0.7    # Sets size of pies
df_pies$height = 0.3   

gg <- ggplot(data=df_range, aes(x, y)) + 
  geom_blank() +
  annotation_map(map_norway_h, aes(long, lat), fill = "darkolivegreen3") +
  geom_subview(aes(x=x, y=y, subview=pie, width=width, height=height), data=df_pies)
# gg
ggsave("Figures/02_Map_elements_01.png", gg, width = 10, height = 11, dpi = 500)
```

### e. SE Norway  
Including labels using ggrepel
```{r, fig.height=7}
# Define two points in lower left and upper right corner (just used to set the drawing canvas)
df_pies$width = 0.3    # Sets size of pies
df_pies$height = 0.15   

xlimits <- c(7,12)
ylimits <- c(58, 60.7)
df_pies_s <- df_pies %>% 
  filter(x > xlimits[1] & x < xlimits[2] &
           y > ylimits[1] & y < ylimits[2])

gg <- ggplot(data=df_range, aes(x, y)) + 
  geom_blank() +
  annotation_map(map_norway_h, aes(long, lat), fill = "darkolivegreen3") +
  geom_subview(aes(x=x, y=y, subview=pie, width=width, height=height), data=df_pies_s) + 
  geom_text_repel(data = df_pies_s, aes(label = label), point.padding = 0.5) +
  coord_cartesian(xlim = xlimits, ylim = ylimits)
ggsave("Figures/02_Map_elements_SE_01.png", gg, width = 10, height = 7, dpi = 500)
# gg
```

### f. W Norway  
Including labels using ggrepel
```{r, fig.height=7}
# Define two points in lower left and upper right corner (just used to set the drawing canvas)
df_pies$width = 0.3    # Sets size of pies
df_pies$height = 0.15   

  # geom_point(data = df_stations %>% filter(Long < 7 & Lat < 63), color = "blue") +
xlimits <- c(4.5, 7.5)
ylimits <- c(58.5, 63)
df_pies_s <- df_pies %>% 
  filter(x > xlimits[1] & x < xlimits[2] &
           y > ylimits[1] & y < ylimits[2])

gg <- ggplot(data=df_range, aes(x, y)) + 
  geom_blank() +
  annotation_map(map_norway_h, aes(long, lat), fill = "darkolivegreen3") +
  geom_subview(aes(x=x, y=y, subview=pie, width=width, height=height), data=df_pies_s) + 
  geom_text_repel(data = df_pies_s, aes(label = label), point.padding = 0.5) +
  coord_cartesian(xlim = xlimits, ylim = ylimits)
ggsave("Figures/02_Map_elements_W_01.png", gg, width = 5, height = 10, dpi = 500)
# gg
```


### g. Troms/Finnmark  
Including labels using ggrepel
```{r, fig.height=7}
# Define two points in lower left and upper right corner (just used to set the drawing canvas)
df_pies$width = 0.3    # Sets size of pies
df_pies$height = 0.15   

  # geom_point(data = df_stations %>% filter(Long < 7 & Lat < 63), color = "blue") +
xlimits <- c(17,31)
ylimits <- c(68, 71)
df_pies_s <- df_pies %>% 
  filter(x > xlimits[1] & x < xlimits[2] &
           y > ylimits[1] & y < ylimits[2])

gg <- ggplot(data=df_range, aes(x, y)) + 
  geom_blank() +
  annotation_map(map_norway_h, aes(long, lat), fill = "darkolivegreen3") +
  geom_subview(aes(x=x, y=y, subview=pie, width=width, height=height), data=df_pies_s) + 
  geom_text_repel(data = df_pies_s, aes(label = label), point.padding = 0.5) +
  coord_cartesian(xlim = xlimits, ylim = ylimits)
ggsave("Figures/02_Map_elements_Finnmark_01.png", gg, width = 8, height = 5, dpi = 500)
# gg
```


### 6. Legend
```{r}
# Note: 'labels' is slighlty change compared to vars
labels <- c("Fisk", "Bunndyr", "Begroingsalger", "Fysisk-kjemiske kvalitetselementer", 
          "Vannregionspesifikke stoffer", "Prioriterte stoffer")
x <- rep(1,6)
names(x) <- vars
pie(x, col = cols, init.angle = 90)
```




