---
title: "04 Kvalitetselementer søylediagram"
output: html_document
---

## 0. Warming up
### a. Lib
```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(viridis)
library(cowplot)     # plot_grid (https://cran.r-project.org/web/packages/cowplot/vignettes/plot_grid.html)

save_plots <- TRUE

```

b. Functions
```{r}
source("04_Kvalitetselementer_søylediagram_functions.R")
```


## 1. Define colours
```{r}
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2)
class_colors <- with(df_colors, rgb(R/255, G/255, B/255))
# class_colors <- c(class_colors, rgb(0.5, 0.5, 0.5))
names(class_colors) <- c("Svært god", "God", "Moderat", "Dårlig", "Svært dårlig","Uklassifisert")
class_colors
```

## 2. Overall indices

### a. Data
```{r}
data_forsur <- read_excel(
  "Data_input/ØkologiskTilstandsklassifisering2017_5nov18.xlsx", 
  sheet = "Forsuring VF", range = "A1:H37", na = "NA")
data_eutrofi <- read_excel(
  "Data_input/ØkologiskTilstandsklassifisering2017_5nov18.xlsx", 
  sheet = " Eutrofi VF ", range = "A1:F37", na = "NA")
data_total <- read_excel(
  "Data_input/ØkologiskTilstandsklassifisering2017_5nov18.xlsx", 
  sheet = "Totalvurdering VF", range = "A1:N37", na = "NA")
```

### b. Acidification , combined index  
Using make_indexplot() function  
```{r}
label <- "Samlet forsuringstilstand (nEQR)"
plotno <- "1a"
gg <- make_indexplot(data_forsur, "Samlet forsurings tilstand", label)
# gg
if (save_plots)
  ggsave(paste0("Figures/04_", plotno, "_", label, ".png"), gg, width = 8.5, height = 10.5, dpi = 500)
```

### c. Eutrophication , combined index  
```{r}
label <- "Samlet eutrofieringstilstand (nEQR)"
plotno <- "1b"
gg <- make_indexplot(data_eutrofi, "Samlet eutrofitilstand", label)
# gg
if (save_plots)
  ggsave(paste0("Figures/04_", plotno, "_", label, ".png"), gg, width = 8.5, height = 10.5, dpi = 500)
```

### d. Combined ecological index  
```{r}
label <- "Samlet økologisk tilstand (nEQR)"
plotno <- "1c"
gg <- make_indexplot(data_total, "Samlet økologisk tilstand", label, varname_navn = "VF, kortnavn")
# gg
if (save_plots)
  ggsave(paste0("Figures/04_", plotno, "_", label, ".png"), gg, width = 8.5, height = 10.5, dpi = 500)
```


## 3. Plots with dots on station/sample level 
With data on station level, using function make_indexplot_dots()    
__NOTE__: Check if this is the latest data  
NOTE: Lacking helper lines for 
```{r}
gg <- make_indexplot_dots("PIT", "PIT-index", "2a")
gg <- make_indexplot_dots("AIP", "AIP-index", "2b", range = "A2:H53", including_kalkrik = TRUE)
gg <- make_indexplot_dots("HBI2", "HBI2-index", "2c")
gg <- make_indexplot_dots("ASPT", "ASPT-index", "2d")
gg <- make_indexplot_dots("RAMI", "RAMI-index", "2e")

```


