---
title: "07 Data for 2024 maps and barplots"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true

---

Plots for data 2024 (report made in 2025)  
* Note: year in script names from 2022 (and earlier) referred to *report year*   
* Get data (used for both maps and figures)   
* These data are used both by scripts 7b, 7c (which also needs some data from 7b), and 7c  
* Things to check when there is a new year:  
    - set year (section 1a2, line 32)  
    - set/check excel cell range (section 2a, line 66)  
    - check number of each class (section 2d) by comparing to excel sheet   


## 1. Prerequisites  

### a1. Libs + map  
```{r}

library(dplyr)       # filter, group_by, summary, etc.
library(readxl)
library(glue)
source("07_Figures_functions.R")

```

### a2. Set year (note: data year)  
```{r}

year <- 2024

```


### a3. Previous year's data for reference
```{r}

# dir.create("Data/2000")
df_index_2021 <- readRDS("Data/2021/07a_df_index_2020.rds")
df_index_barplot_2021 <- readRDS("Data/2021/07a_df_index_barplot_2020.rds")
df_stations_2021 <- readRDS("Data/2021/07a_df_stations_2020.rds")

```


## 2. Data
### a. Read station data (coordinates) for all sample sites  
These are from   
- 2019: `K:\Prosjekter\Ferskvann\16384 Elveovervåkingsprogrammet\2019\Opsjon 3 biologi\Figurer og Kart (Dag)`   
- 2020: `K:\Prosjekter\Ferskvann\16384 Elveovervåkingsprogrammet\2020\Biologi - Opsjon 3\Rapportering\Kart og figurer, Dag` 
```{r}

# Backup (for reproducibility)
dir_data <- glue("Data_input/{year}")    
filename <- glue("KartOgFigurgrunnlag{year}.xlsx")

# Original (used in report):
# dir_data <- "K:/Prosjekter/Ferskvann/16384 Elveovervåkingsprogrammet/2020/Biologi - Opsjon 3/Rapportering/Kart og figurer, Dag"
# filename <- "KartOgFigurgrunnlag_TilDag.xlsx"

excel_sheets(paste0(dir_data, "/", filename))

df_stations_check <- read_excel(paste0(dir_data, "/", filename),
                              sheet = glue("Kartgrunnlag{year}"),
                              # range = "A1:E40",                     # HARD-CODED!
                              col_types = "text")
df_stations_all <- read_excel(paste0(dir_data, "/", filename),
                              sheet = glue("Kartgrunnlag{year}"),
                              # range = "A1:E40",                     # HARD-CODED!
                              col_types = "text") %>%
  rename(Shortname = Rapportnavn,
         Lat = Biologi_Lat,
         Long = Biologi_Long,
         Index_ecol = `Samlet økologisk tilstand (nEQR)`,
         Class_chem = `Kjemisk tilstand`) %>%
  select(Shortname, Lat, Long, Index_ecol, Class_chem) %>% 
  as.data.frame()

# If any of the following columns are not numeric (typically because of 
# decimal comma instead of decimal point), try to change them to numeric
for (i in c("Lat", "Long", "Index_ecol")){
  if (class(df_stations_all[[i]]) != "numeric"){
    number_of_NAs_before <- sum(is.na(df_stations_all[,i]))
    # Replace ',' with '.' and convert to numeric
    x <- sub(",", ".", df_stations_all[,i], fixed = TRUE)
    x <- as.numeric(x)
    number_of_NAs_after <- sum(is.na(x))
    if (number_of_NAs_after > number_of_NAs_before){
      stop("For some values, it didn't work to replace ',' with '.' and convert to numeric. Check data!")
    } else {
      df_stations_all[,i] <- x
    }
  }
}

# Fix NUM0 position error
# NOT NEEDED THIS YEAR
# sel <- grepl("NUM0", df_stations_all$Shortname); sum(sel)
# df_stations_all$Breddegrad[sel] <- "59.085689"

# "Fill out" Shortname
# NOT NEEDED THIS YEAR
# for (i in  2:nrow(df_stations_all)){
#   if (is.na(df_stations_all$Shortname[i]))
#     df_stations_all$Shortname[i] <- df_stations_all$Shortname[i-1]
# }

df_stations_all

```

### b. Make 'df_stations'  
Condensing to one line per station (not needed this year)    
The mining stations ('Gruve') not included from 2022 onwards
```{r}

df_stations <- df_stations_all %>%
  # 2021 code deleted here (condensing to one line per station)
  mutate(
    Stasjonstype = case_when(
      !is.na(Index_ecol) & is.na(Class_chem) ~ "Økologisk tilstand",
      !is.na(Index_ecol) & Class_chem %in% c("i.d.", "ID") ~ "Økologisk tilstand",
      !is.na(Index_ecol) & Class_chem != c("i.d.", "ID") ~ "Økologisk og kjemisk tilstand",
      grepl("^Gruve", Shortname) ~ "Gruvevassdrag (lange tidsserier)",
      TRUE ~ "?"),
    Stasjonstype = factor(Stasjonstype, 
                          levels = c(
                            "Økologisk og kjemisk tilstand", "Økologisk tilstand"))
  )

xtabs(~addNA(Stasjonstype) + addNA(Class_chem), df_stations)

```

### c. Read data for bar plots  
* df_index is the actual data  
* df_index_barplot will be used for bar plots (see remark in comments)
```{r}
# readxl::excel_sheets("Data_input/2022/Klassifisering av økologisk tilstand i elver for rapport 2020.xlsx")

df_check <- read_excel(
  paste0(dir_data, "/", filename),
  na = "NA",
  sheet = glue("Figurgrunnlag{year}"))

df_index <- read_excel(
  paste0(dir_data, "/", filename),
  na = "NA",
  col_types = c("text", "numeric", "text", "text"), 
  sheet = glue("Figurgrunnlag{year}")
) %>% 
  rename(nEQR_ecol = `Samlet økologisk tilstand (nEQR)`) %>% 
  select(Rapportnavn, nEQR_ecol) %>% 
  as.data.frame()

# only nEQR_ecol this year
df_index <- df_index %>% 
  mutate(nEQR_eutrofi = as.numeric(NA), nEQR_forsuring = as.numeric(NA))

df_index <- df_index %>% filter(!is.na(Rapportnavn))

# Note: in 'make_indexplot()', the name "Rapportnavn" is hard-coded

# nEQR shouldn't be > 1
# df_index <- df_index %>%
#   mutate(nEQR_forsuring = ifelse(nEQR_forsuring > 1, 1, nEQR_forsuring))

df_index

# Data for barplots
df_index_barplot <- df_index

# Data for barplots (2020, ie. 2019 data)
# "27.ORK1" has a missing value for 'nEQR_ecol', but it is supposed to be 'Moderate' 
#   with 'unapplicable' nEQR_ecol. We here setr it to 0.5 jsut to have something to plot 

# df_index_barplot <- df_index %>%
#   mutate(nEQR_ecol =
#            case_when(Rapportnavn %in% "27.ORK1" ~ 0.5,
#                      TRUE ~ nEQR_ecol)
#          ) %>%
#   mutate(Label =
#            case_when(Rapportnavn %in% "27.ORK1" ~ paste(Rapportnavn, "(nEQR-verdi ikke gjeldende)"),
#                      TRUE ~ Rapportnavn)
#          )
  

```

### d. Add class value to bar plots    

* As the "class data" in the excel sheet is cell colour, check table and compare with number of different colors in the excel sheet "check colors"!  

```{r}


# names(df_index_barplot) %>% dput()

# vars <- c("nEQR_eutrofi", "nEQR_forsuring", "nEQR_ecol")
vars <- "nEQR_ecol"

for (var in vars){
  x1 <- df_index_barplot[[var]]
  x2 <- 6 - as.numeric(cut(x1, breaks =  seq(0,1,0.2) + 0.001, label = FALSE))
  x3 <- c("Svært god", "God", "Moderat", "Dårlig", "Svært dårlig", "Uklassifisert")[x2]
  x3[is.na(x3)] <- "Uklassifisert"
  
  # Make variable 'Class'
  df_index_barplot$Class <- factor(x3, levels = c("Svært god", "God", "Moderat", 
                                                "Dårlig", "Svært dårlig", "Uklassifisert"))
  
  # Change name of variable 'Class'
  df_index_barplot <- rename2(
    df = df_index_barplot, 
    oldname = "Class",
    newname = paste0(var, "_klasse")
    )

}


# Tabulate the result
df_index_barplot %>%
  # First, put the data on long format
  # dplyr::select(Rapportnavn, nEQR_eutrofi_klasse, 
  #               nEQR_forsuring_klasse, nEQR_ecol_klasse) %>%
  dplyr::select(Rapportnavn, nEQR_ecol_klasse) %>%
  tidyr::pivot_longer(
    cols = -Rapportnavn,
    names_to = "Type", values_to = "Class") %>%
  # Then make table  
  xtabs(~Type + addNA(Class), .)

#
# Checked with excel, by sorting the excel and counting cells by colour
#

```

### e. Change index value for one salt water influenced station  
```{r}

if (FALSE){
  
  sel <- grepl("STR1", df_index_barplot$Rapportnavn)
  cat(sum(sel), "station chosen \n")
  
  df_index_barplot$nEQR_eutrofi_klasse[sel] <- "Uklassifisert"
  df_index_barplot$nEQR_forsuring_klasse[sel] <- "Uklassifisert"
  df_index_barplot$nEQR_ecol_klasse[sel] <- "Uklassifisert"
  
  cat("Class set to NA for station",  sQuote(df_index_barplot$Rapportnavn[sel]), "  \n")
  
}


```

Stations  
```{r}
df_stations$Shortname
```


## 3. Save  
```{r}

# dir.create("Data/2022")

folder_save <- glue("Data/{year}")
if (!dir.exists(folder_save))
  dir.create(folder_save)

saveRDS(df_index, glue("Data/{year}/07a_df_index_{year}.rds"))
saveRDS(df_index_barplot, glue("Data/{year}/07a_df_index_barplot_{year}.rds"))
saveRDS(df_stations, glue("Data/{year}/07a_df_stations_{year}.rds"))

```

## 4. Appendix - check leaflet map  

```{r}

# library(leaflet)
leaflet(df_stations) %>% 
  leaflet::addTiles() %>% 
  leaflet::addMarkers(lng = ~Long, lat = ~Lat, popup = ~Shortname)


```

