---
title: "07 Figures 2018 - maps and barplots"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true

---

Plots for report 2020 (*data* from 2019!)   
* Get data (used for both maps and figures)   
* These data are used both by scripts 7b, 7c (which also needs some data from 7b), and 7c  


## 1. Prerequisites  

### a1. Libs + map  
```{r}

library(dplyr)       # filter, group_by, summary, etc.
library(readxl)
source("07_Figures_functions.R")


```



## 2. Data
### a. Read station data (coordinates) for all sample sites  
These are from   
`K:\Prosjekter\Ferskvann\16384 Elveovervåkingsprogrammet\2019\Opsjon 3 biologi\Figurer og Kart (Dag)`  
```{r}
df_stations_all <- read_excel(
  "Data_input/2020/KartOgFigurgrunnlag_TilDag.xlsx", 
  sheet = "Kartgrunnlag")
df_stations_all <- df_stations_all[1:5]
names(df_stations_all)[c(1,4,5)] <- c("Shortname", "Index_ecol", "Class_chem")

# Set long, lat
df_stations_all <- df_stations_all %>%
  mutate(Lat = as.numeric(sub(",", ".", Breddegrad)),
         Long = as.numeric(sub(",",".", Lengdegrad))
         )

# "Fill out" Shortname
for (i in  2:nrow(df_stations_all)){
  if (is.na(df_stations_all$Shortname[i]))
    df_stations_all$Shortname[i] <- df_stations_all$Shortname[i-1]
}

df_stations_all
```

### b. Make 'df_stations'  
Condensing to one line per station    
The mining stations ('Gruve') have NA for both Index_ecol and Class_chem
```{r}

df_stations <- df_stations_all %>%
  group_by(Shortname) %>%
  summarise(Long = mean(Long),
            Lat = mean(Lat),
            Index_ecol = first(Index_ecol),
            Class_chem = first(Class_chem)) %>% # View()
  mutate(
    Stasjonstype = case_when(
      !is.na(Index_ecol) & is.na(Class_chem) ~ "Økologisk tilstand",
      !is.na(Index_ecol) & Class_chem %in% "i.d." ~ "Økologisk tilstand",
      !is.na(Index_ecol) & Class_chem != "i.d." ~ "Økologisk og kjemisk tilstand",
      grepl("^Gruve", Shortname) ~ "Gruvevassdrag (lange tidsserier)",
      TRUE ~ "?"),
    Stasjonstype = factor(Stasjonstype, 
                          levels = c(
                            "Økologisk og kjemisk tilstand", "Økologisk tilstand",
                            "Gruvevassdrag (lange tidsserier)"))
  )

xtabs(~addNA(Stasjonstype) + addNA(Class_chem), df_stations)

```

### c. Read data for bar plots  
* df_index is the actual data  
* df_index_barplot will be used for bar plots (see remark in comments)
```{r}
df_index <- read_excel("Data_input/2020/KartOgFigurgrunnlag_TilDag.xlsx", 
                       sheet = "Figurgrunnlag",
                       na = "NA", 
                       col_types = c("text", rep("numeric",3))) 

names(df_index) <- c("Rapportnavn", "nEQR_eutrofi", "nEQR_forsuring", "nEQR_ecol") # NOTE: hard-coded

df_index <- df_index %>% filter(!is.na(Rapportnavn))

# Note: in 'make_indexplot()', the name "Rapportnavn" is hard-coded

# nEQR shouldn't be > 1
df_index <- df_index %>%
  mutate(nEQR_forsuring = ifelse(nEQR_forsuring > 1, 1, nEQR_forsuring))

df_index

# Data for barplots
# "27.ORK1" has a missing value for 'nEQR_ecol', but it is supposed to be 'Moderate' 
#   with 'unapplicable' nEQR_ecol. We here setr it to 0.5 jsut to have something to plot 
df_index_barplot <- df_index %>%
  mutate(nEQR_ecol =
           case_when(Rapportnavn %in% "27.ORK1" ~ 0.5,
                     TRUE ~ nEQR_ecol)
         ) %>%
  mutate(Label =
           case_when(Rapportnavn %in% "27.ORK1" ~ paste(Rapportnavn, "(nEQR-verdi ikke gjeldende)"),
                     TRUE ~ Rapportnavn)
         )
  

```

### d. Add class value to bar plots  
```{r}


# names(df_index_barplot) %>% dput()

for (var in c("nEQR_eutrofi", "nEQR_forsuring", "nEQR_ecol")){
  x1 <- df_index_barplot[[var]]
  x2 <- 6 - as.numeric(cut(x1, breaks =  seq(0,1,0.2) + 0.001, label = FALSE))
  x3 <- c("Svært god", "God", "Moderat", "Dårlig", "Svært dårlig", "Uklassifisert")[x2]
  
  # Make variable 'Class'
  df_index_barplot$Class <- factor(x3, levels = c("Svært god", "God", "Moderat", 
                                                "Dårlig", "Svært dårlig", "Uklassifisert"))
  
  # Change name of variable 'Class'
  df_index_barplot <- rename2(
    df = df_index_barplot, 
    oldname = "Class",
    newname = paste0(var, "_klasse")
    )

}

# Tabulate the result
df_index_barplot %>%
  # First, put the data on long format
  select(Rapportnavn, nEQR_eutrofi_klasse, nEQR_forsuring_klasse, nEQR_ecol_klasse) %>%
  tidyr::pivot_longer(
    cols = -Rapportnavn,
    names_to = "Type", values_to = "Class") %>%
  # Then make table  
  xtabs(~Type + Class, .)
      

```

### e. Change index value for one salt water station  
```{r}

sel <- grepl("STR1", df_index_barplot$Rapportnavn)
cat(sum(sel), "station chosen \n")

df_index_barplot$nEQR_eutrofi_klasse[sel] <- "Uklassifisert"
df_index_barplot$nEQR_forsuring_klasse[sel] <- "Uklassifisert"
df_index_barplot$nEQR_ecol_klasse[sel] <- "Uklassifisert"

cat("Class set to NA for station",  sQuote(df_index_barplot$Rapportnavn[sel]), "  \n")


```

Stations  
```{r}
df_stations$Shortname
```


## 3. Save  
```{r}

# dir.create("Data/2000")
saveRDS(df_index, "Data/2020/07a_df_index_2019.rds")
saveRDS(df_index_barplot, "Data/2020/07a_df_index_barplot_2019.rds")
saveRDS(df_stations, "Data/2020/07a_df_stations_2019.rds")

```

