---
title: "07 Figures 2018 - maps and barplots"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true

---

Plots for report 2020 (*data* from 2019!)   
* Get data (used for both maps and figures)  


## 1. Prerequisites  

### a1. Libs + map  
```{r}
library(dplyr)       # filter, group_by, summary, etc.
library(readxl)

```



## 2. Data
### a. Read station data (coordinates) for all sample sites
```{r}
df_stations_all <- read_excel(
  "Data_input/2020/KartOgFigurgrunnlag_TilDag.xlsx", 
  sheet = "Kartgrunnlag")
df_stations_all <- df_stations_all[1:5]
names(df_stations_all)[c(1,4,5)] <- c("Shortname", "Index_ecol", "Class_chem")

# Set long, lat
df_stations_all <- df_stations_all %>%
  mutate(Lat = as.numeric(sub(",", ".", Breddegrad)),
         Long = as.numeric(sub(",",".", Lengdegrad))
         )

# "Fill out" Shortname
for (i in  2:nrow(df_stations_all)){
  if (is.na(df_stations_all$Shortname[i]))
    df_stations_all$Shortname[i] <- df_stations_all$Shortname[i-1]
}

df_stations_all
```

### b. Make 'df_stations'  
Condensing to one line per station    
The mining stations ('Gruve') have NA for both Index_ecol and Class_chem
```{r}

df_stations <- df_stations_all %>%
  group_by(Shortname) %>%
  summarise(Long = mean(Long),
            Lat = mean(Lat),
            Index_ecol = first(Index_ecol),
            Class_chem = first(Class_chem)) %>%
  mutate(
    Stasjonstype = case_when(
      !is.na(Index_ecol) & Class_chem %in% "i.d." ~ "Økologisk tilstand",
      !is.na(Index_ecol) & Class_chem != "i.d." ~ "Økologisk og kjemisk tilstand",
      grepl("^Gruve", Shortname) ~ "Gruvevassdrag (lange tidsserier)",
      TRUE ~ "?"),
    Stasjonstype = factor(Stasjonstype, 
                          levels = c(
                            "Økologisk og kjemisk tilstand", "Økologisk tilstand",
                            "Gruvevassdrag (lange tidsserier)"))
  )

xtabs(~Stasjonstype + addNA(Class_chem), df_stations)

```

### c. Read data for bar plots  
* df_index is the actual data  
* df_index_barplot will be used for bar plots (see remark in comments)
```{r}
df_index <- read_excel("Data_input/2020/KartOgFigurgrunnlag_TilDag.xlsx", 
                       sheet = "Figurgrunnlag",
                       na = "NA", 
                       col_types = c("text", rep("numeric",3))) 

names(df_index) <- c("Rapportnavn", "nEQR_eutrofi", "nEQR_forsuring", "nEQR_ecol") # NOTE: hard-coded

df_index <- df_index %>% filter(!is.na(Rapportnavn))

# Note: in 'make_indexplot()', the name "Rapportnavn" is hard-coded

# nEQR shouldn't be > 1
df_index <- df_index %>%
  mutate(nEQR_forsuring = ifelse(nEQR_forsuring > 1, 1, nEQR_forsuring))

df_index

# Data for barplots
# "27.ORK1" has a missing value for 'nEQR_ecol', but it is supposed to be 'Moderate' 
#   with 'unapplicable' nEQR_ecol. We here setr it to 0.5 jsut to have something to plot 
df_index_barplot <- df_index %>%
  mutate(nEQR_ecol =
           case_when(Rapportnavn %in% "27.ORK1" ~ 0.5,
                     TRUE ~ nEQR_ecol)
         ) %>%
  mutate(Label =
           case_when(Rapportnavn %in% "27.ORK1" ~ paste(Rapportnavn, "(nEQR-verdi ikke gjeldende)"),
                     TRUE ~ Rapportnavn)
         )
  

```


Stations  
```{r}
df_stations$Shortname
```


## 3. Save  
```{r}

# dir.create("Data/2000")
saveRDS(df_index, "Data/2020/07a_df_index_2019.rds")
saveRDS(df_index_barplot, "Data/2020/07a_df_index_barplot_2019.rds")
saveRDS(df_stations, "Data/2020/07a_df_stations_2019.rds")

```

