---
title: "07 Figures 2018 - maps and barplots"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true

---

Overview maps (types of stations) for Methods chapter (section 3)  
* using UTM zone 32V as projection  
* Data for 7c are saved in 4c   
* "Lange tidsserier" ('long time-series' stations) are used for Methods map, not in Results  

## Overview of process:    
1. Packages and load scripts      
2. Data, includes    
    - station data  
    - background map (coast- + county lines)  
    - rivers  
    - the last two: downloaded as shape (UTM33), but coordinares extracted and converted to UTM32  
3. Defines inset map boxes using a leaflet map; therefore boxes are defined using lat/long  
    - boxes are saved as a list, each of which defining bottom left and top right corner   
4. Prepare data sets in UTM32  
    - station data   
    - box_corners (used to make the inset plots, 'make_subplot_nolabels', and to filter stations for these)
    - box_polygons (used to plot inset rectangles on the big map, 6b)  
5. Is used only as a fast way to make a draft map with labels (used as help for 6a)
6. Build gg3a plot
    - Build gg2_points plot based on background map (gg_back + rivers) + labels, group by group  
    - gg3a map = gg2_points map plus boxes   
7. Functions for making insets  
8. Make insets including labels. the resukt is a list of ggplot objects)
9. Make final plot by adding legend (gg3b), then plot gg3b plus each of the insets   
    - position of insets is quite a bit try and error   

## Overview of some important objects and where they are created      

Box coordinates:    
- 3a2: boxlist, with lat-lon("manually" made by testing leaf2 in 3-c)  
- 4b: 'boxlist' -> 'box_polygons' (UTM coordinates + dimensions)
- 6b: box_polygons -> box_letter_pos   
  
ggplots (gg):  
- 6a: gg_back -> gg2 (adding points and labels outside boxes)
- 6b: gg2 -> gg3a (adding boxes and letters)   
- 8: gg_back + df_stations -> gg_box 1-4 (adding rivers, points, labels)
- 9b: 
    - gg3a -> gg3b (removing legend)  
    - gg3b + gg_box -> gg4 (adding inset maps) 

data:  
- 2a1: df_stations_all (read)
- 2a3: df_stations_all -> df_stations (So. Norway only)  
- 4a: df_stations -> df_stations (adding UTM coordinates)
- 5a: df_stations + boxlist -> df_stations_outside (only used for test plots)  
  
Plots are combined and written to file in a separate script:   
`07b_Figures_2020_labelmap_combine.R`  


## 1. Prerequisites  

### a. Whether and where to save figures  
```{r}
#
# Save figures to file, or just show them in this report?
#
# NOTE: we now use a separate R file (see 9b in this script) 
# - `07b_Figures_2020_labelmap_combine.R`  
#
# save_plots <- TRUE
save_plots <- FALSE


#
# Where to save figures
#
folder_fig <- "Figures/2022_main"


```

### b. Packages + map  
```{r}

library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(mapdata)
library(readxl)

# map_norway <- map_data("world", "Norway")
# map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

# Long/lat map (including the smaller islands) - lacking Mjøsa, though! 
#   (and including some North Finnish lakes?)
load("Data_input/Norway_coastline_longlat2.RData")
# rename
map_norway_h <- norway_coast_longlat2
rm(norway_coast_longlat)

# Test plot
# ggplot(map_norway_h) + geom_path(aes(long, lat, group = group))

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()
library(sp)         # SpatialPoints(), CRS(), spTransform()
library(sf)         # st_read
library(ggimage)    # geom_subview(), theme_transparent()

library(glue)       # used in ggplot2() function
library(leaflet)

library(cowplot)

library(scatterD3)  # used to position labels  

source("07_Figures_functions.R")

# Define crs strings for conversion between long/lat and UTM
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"  # note: zone 32

```


## 2. Data

### a1. Data   
* From excel  
```{r, warning=FALSE}

# df_stations_all_OLD <- readRDS("Data/2021/07a_df_stations_2020.rds")
# str(df_stations_all_OLD)

df_stations_all <- readRDS("Data/2022/07a_df_stations_2021.rds")


if (FALSE){
  
  # For reading from excel 
  coltypes <- c("text", "numeric", "numeric", "numeric", "text")
  df_stations_all <- read_excel("Data_input/2022/KartOgFigurgrunnlag2021.xlsx", 
                                range = "A1:E34", 
                                col_types = coltypes) %>%
    rename(Shortname = Rapportnavn,
           Lat = Biologi_Lat,
           Long = Biologi_Long)

  str(df_stations_all)
  
}



```

### a2. Stations, add UTM coordinates
```{r}

# The default transformation for 'add_transformed_coord' is from latlong to 
df_stations_all <- add_transformed_coord(df_stations_all, 
                                     name_x = "Long", name_y = "Lat",
                                     from = "longlat", to = "utm", to_zone = 32)  

write_csv(df_stations_all %>% select(-Stasjonstype),
          "Data_input/2022/KartOgFigurgrunnlag2021.csv")  

# write_csv(very_simple_map %>% add_transformed_coord(),
#           "Data_input/2022/very_simple_map.csv")

```

### a3. Plot all stations  
```{r}

df_stations_all$Stasjonstype %>% table()

very_simple_map <- map_data("world", "Norway")

ggplot(df_stations_all, aes(Long, Lat, color = Stasjonstype)) +
  annotation_map(very_simple_map, fill = "lightgreen") +
  geom_point() +
  # geom_text_repel() +
  coord_map("lambert", 15, 65)  


```

### a4. Split into North and South Norway    

```{r}

df_stations_south <- df_stations_all %>%
  filter(Lat < 65)

df_stations_north <- df_stations_all %>%
  filter(Lat >= 65)

if (TRUE){
  
  ggplot(df_stations_south, aes(Long, Lat, color = Stasjonstype)) +
    annotation_map(very_simple_map, fill = "lightgreen") +
    geom_point() +
    # geom_text_repel() +
    coord_map("lambert", 15, 65) 
  
  ggplot(df_stations_north, aes(Long, Lat, color = Stasjonstype)) +
    annotation_map(very_simple_map, fill = "lightgreen") +
    geom_point() +
    # geom_text_repel() +
    coord_map("lambert", 15, 65) 
  
}

```


### b1. Map with counties (fylke)   

* 
```{r}
# 
# Gotten from Geonorge ("Norske fylker og kommuner illustrasjonsdata 2019 (klippet etter kyst)")
#   https://kartkatalog.geonorge.no/metadata/cb02ab77-d3e6-4500-8a92-ea67367e7734 
#   https://nedlasting.geonorge.no/geonorge/Generell/AdmEnh_klippet_etter_kyst2019.zip  
map_counties_utm33 <- sf::st_read("Data_input/2021_map/fylker2021.json")
# UTM zone 33
# plot(map_counties_utm)

```

### b2. Make simplified coastline  
* Using 'st_simplify'  
    - reduces size from 17 MB to 0.6 MB  
    - see https://www.r-bloggers.com/2021/03/simplifying-geospatial-features-in-r-with-sf-and-rmapshaper/   
    - The simplification changes the geometry column from MULTIPOLYGON to GEOMETRY,
    we must change it back (otherwise `st_coordinates`doesn't work)  
    - See https://cran.r-project.org/web/packages/sf/vignettes/sf3.html  

```{r}

map_counties_utm33_simple <- st_simplify(map_counties_utm33,
                                         preserveTopology = FALSE, dTolerance = 500)

# The simplification () changes the geometry column from to GEOMEtry
# Check:
# class(map_counties_utm33$geometry)         # "sfc_MULTIPOLYGON" "sfc"
# class(map_counties_utm33_simple$geometry)  # "sfc_GEOMETRY" "sfc"
# We change it back like this: 
#  (ref: https://cran.r-project.org/web/packages/sf/vignettes/sf3.html)

map_counties_utm33_simple$geometry <- st_cast(
  map_counties_utm33_simple$geometry, "MULTIPOLYGON")

```

### c. Get coordinates of county map (df_counties_all)  
Used to make the background map  
* We convert the map from UTM zone 33 to UTM 32, as this is more fitting for Southern Norway   (https://upload.wikimedia.org/wikipedia/commons/9/9e/LA2-Europe-UTM-zones.png)
```{r}

map_to_dataframe <- function(map_object){
  st_coordinates(map_object) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2, id = L3)
}

# Extract coordinates and Transform from UTM33 to UTM32
df_counties_all <- map_to_dataframe(map_counties_utm33)
df_counties_all_simple <- map_to_dataframe(map_counties_utm33_simple)

nrow(df_counties_all)
nrow(df_counties_all_simple)
# [1] 798273
# [1] 20095
```



### d. Make background map (gg1_back)    
```{r}

# Check counties: it turns out that 5 = Nordland, 10 = Troms + Finnmark

if (FALSE){
  df_counties_all %>% 
    filter(L1 == 1) %>%
    group_by(id) %>%
    summarise(across(, mean)) %>%
    arrange(y) %>%
    ggplot(aes(x, y, label = id)) +
    geom_text() +
    coord_equal(ratio = 0.5) 
}

# Keep these 4 counties (Trøndelag + Nordland)
# - for both full and simple version
df_counties_full <- df_counties_all %>%
  filter(id %in% c(9,5,6,11))
df_counties_simp <- df_counties_all_simple %>%
  filter(id %in% c(9,5,6,11))

# Get remaining county numbers
county_numbers <- unique(df_counties_simp$id)

# Make gg 

gg_from_counties_coastline <- function(mapdata){
  
  result <- ggplot(data = mapdata, aes(x, y)) + 
    geom_blank() + 
    coord_fixed() +
    theme_minimal() +
    theme(panel.grid = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
    )
  
  # Add one county after the other
  for (i in county_numbers){
    result <- result + 
      geom_polygon(data = mapdata %>% filter(L1 == 1 & id %in% i), 
                   aes(x, y, group = group), fill = "navajowhite", color = "grey30")
  }
  
  invisible(result)
  
}

# Start 'gg_back_full'
gg_back_full <- gg_from_counties_coastline(df_counties_full)
gg_back_simp <- gg_from_counties_coastline(df_counties_simp)

# test use of ggdata
if (FALSE)
  gg_back_simp + ylim(range(ggdata$y) + c(-100E3, 0))

```

### e1. Rivers

```{r}

nc_rivers_strahler4_full <- st_read(
  "K:\\Kart\\ELVIS\\Hovedelv\\elvis_hovedelv.shp",
  query = "SELECT * FROM elvis_hovedelv WHERE STRAHLER >= 4")  # only big rivers; saves a little time
#  UTM zone 33

# Turns out to be harder to simplify rivers (they fall apart...)
simplify_rivers <- FALSE  
# simplify_rivers <- TRUE  

if (simplify_rivers){
  
  nc_rivers_strahler4 <- st_simplify(nc_rivers_strahler4_full,
                                     preserveTopology = FALSE, dTolerance = 100)
  # Check class of geometry:
  # nc_rivers_strahler4_full[["_ogr_geometry_"]][1] %>% class()
  nc_rivers_strahler4[["_ogr_geometry_"]] <- st_cast(
    nc_rivers_strahler4[["_ogr_geometry_"]], "MULTILINESTRING")
  
} else {
  
  nc_rivers_strahler4 <- nc_rivers_strahler4_full
  
}

# Extract coordinates and Transform from UTM33 to UTM32
df_rivers_strahler5 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 5) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000)  # Fix errors (i.e. remove extremely long segments)

df_rivers_strahler6 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 6) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000) # Fix errors (i.e. remove extremely long segments)

df_rivers_strahler7 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 7) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000) # Fix errors (i.e. remove extremely long segments)

range(df_counties_full$y)
south_limit <- min(df_counties_full$y) - 300000 # 300 km S and N of limits
north_limit <- max(df_counties_full$y) + 300000

# Remove data for North Norway (filter doesn't work, as some data are reshuffeled)
# sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y < south_limit  
# df_rivers_strahler5[sel, c("x","y")] <- NA
# sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y > north_limit  
# df_rivers_strahler5[sel, c("x","y")] <- NA
# 
# sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y < south_limit
# df_rivers_strahler7[sel, c("x","y")] <- NA
# sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y > north_limit
# df_rivers_strahler7[sel, c("x","y")] <- NA

rivercol <- "lightskyblue"

```

### e2 Plot rivers  
```{r}

if (TRUE){
  
  # Test plot
  gg_back_simp +
    geom_path(data = df_rivers_strahler6, aes(x, y, group = group), col = "red") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))
}
  
if (FALSE){

  gg_back_simp +
    geom_path(data = df_rivers_strahler6_full, aes(x, y, group = group), col = "red") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))

}

```

### f1. Lakes  

Get coordinates (in zone 32)   
```{r}

nc_lakes_full <- st_read("K:/Kart/N1000/VANN.shp")
st_crs(nc_lakes_full) <- "+proj=utm +zone=33"  # set coordinate system

# Turns out to be harder to simplify rivers (they fall apart...)
simplify_lakes <- FALSE  
# simplify_lakes <- TRUE  

if (simplify_lakes){
  
  nc_lakes <- st_simplify(nc_lakes_full,
                                     preserveTopology = FALSE, dTolerance = 300)
  # Check class of geometry:
  # nc_lakes[["_ogr_geometry_"]][1] %>% class()
  nc_lakes[["geometry"]] <- st_cast(
    nc_lakes[["geometry"]], "POLYGON")
  
} else {
  
  nc_lakes <- nc_lakes_full
  
}

# Extract coordinates and Transform from UTM33 to UTM32
df_lakes <- st_coordinates(nc_lakes) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2)

# Mjøsa only 
df_lakes_mjosa <- df_lakes %>% filter(group == 3462)

```


### f2. Plot lakes    
```{r}

if (TRUE){
  
  # Test plot
  gg_back_simp +
    geom_polygon(data = df_lakes, aes(x, y, group = group), col = "red", fill = "blue3") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))
}
  
```


## 3. Plot with labels via ggrepel + scatterD3

* without inset boxes   
* Not used - turn out to be more complex than needed  

### a. ggrepel plot  
```{r, fig.width=8, fig.height=10}

df_stations         <- df_stations_all   
df_stations_outside <- df_stations_all   

gg1 <- gg_back_simp +
  geom_point(
    data = df_stations, 
    aes(label = Shortname, shape = Stasjonstype)) +
  theme(  legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.box.background = element_rect(fill = "white", color = NA), 
          legend.margin = margin(6, 6, 6, 6),
          legend.key = element_rect(fill = "white", color = NA),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 18)
  ) +
  geom_text_repel(
    data = df_stations_outside, 
    aes(label = Shortname, shape = Stasjonstype), color = "blue3", 
    hjust = 0, force = 1, force_pull = 0.4, nudge_x = 50000, box_padding = 0.5,
    point_padding = 0.5)

if (save_plots)
  ggsave2("{folder_fig}/07b_labelmap_test.png", gg1, width = 8, height = 12)

# gg1

```
### b. Manual label placement using scatterD3

* Work flow  
    - code was run in the console   
    - plot opens in the View window of RStudio  esize util it fits actual aspect of the map  
    - labels adjusted manually (drag with mouse). Concentrate on the labels itself, not the lines  
    - then click cogwheel icon in top right of map and choose "Export label positons"  
    - saved in `Data_input\2022` as `Referanseelver_labels_2021.csv`   
    - run next chunk (`c. Plot using exported label placement`) and repeat process if necessary  
    - one problem is that label adjustment is not saved  
```{r, fig.width = 4, fig.height = 9}

# doesn't work for tibbles, so we convert it:
df_stations <- as.data.frame(df_stations) 

# test in Rmd
# better to run in console and to do label placement in the Viewer
scatterD3(data = df_stations, x = x, y = y, lab = Shortname)

```


### c. Plot using exported label placement  

```{r, fig.width=8, fig.height=10}

df_labels <- read.csv("Data_input/2022/Referanseelver_labels_2021_v2.csv")

df_labels <- df_labels %>%
  mutate(
    adjustment_h = case_when(
        grepl("ORK", lab) ~ 1,
        TRUE ~ 0),
    lab_x_adj = case_when(
        grepl("ORK", lab) ~ lab_x -13000,
        TRUE ~ lab_x + 13000)
  )
  
df_stations         <- df_stations_all %>%
  left_join(df_labels, by = c("Shortname" = "lab"))

gg1 <- gg_back_simp +
  geom_point(
    data = df_stations, 
    aes(label = Shortname, shape = Stasjonstype)) +
  geom_text(data = df_labels, aes(x = lab_x_adj, y = lab_y, label = lab,
                                  hadj = adjustment_h), 
            color = "red", size = rel(3)) +
  theme(  legend.position = c(.05, .95),
          legend.justification = c("left", "top"),
          legend.box.just = "left",
          legend.box.background = element_rect(fill = "white", color = NA), 
          legend.margin = margin(6, 6, 6, 6),
          legend.key = element_rect(fill = "white", color = NA),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 18)
  )

gg1b <- gg_back_simp +
  scale_x_continuous(breaks = seq(400000, 800000, by = 50000), 
                     minor_breaks = seq(400000, 800000, by = 10000)) +
  scale_y_continuous(breaks = seq(6.9E6, 7.5E6, by = 50000), 
                     minor_breaks = seq(6.9E6, 7.5E6, by = 10000)) +
  theme(panel.grid.major = element_line(size = 1))  

gg1c <- gg1 +
  coord_fixed(xlim = c(400000, 800000), ylim = c(6.95E6, 7.5E6))

if (save_plots)
  ggsave2("{folder_fig}/07b_labelmap_test.png", gg1c, width = 8, height = 12)

gg1c

```

### d. Export as svg   

* Edit in Inkscape  
    - When you open the figure, all objects are grouped; select Object:Ungroup  
    - Now labels can be moved manually  
    - Mouse wheel to move up/down, shift + mouse wheel to move left/right  
    - To edit text, use Text Tool (use arrow tool to resize object if needed)  
    - To add lines, use Bezier and Straight lines tool (left click for each end, right click for finishing). Use shift + click on the colors on the bottom to change line color  
    - Saved as `07b_labelmap_adj01.svg` and `07b_labelmap_adj02.svg`   

```{r}

ggsave2("{folder_fig}/07b_labelmap_test.svg", gg1, width = 8, height = 12)

```


## 4. Plot with labels, not ggrepel + scatterD3    

#### Make a ggplot without labels and save as svg

```{r, fig.width=8, fig.height=10}

gg_back_simp +
  theme(panel.grid.major.x = )

gg1 <- gg_back_simp +
  geom_path(data = df_rivers_strahler5, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol) +
  geom_point(
    data = df_stations, 
    aes(shape = Stasjonstype, fill = Stasjonstype), size = rel(2)) +
  scale_fill_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21,22,24)) +
  theme(  legend.position = c(.05, .95),
          legend.justification = c("left", "top"),
          legend.box.just = "left",
          legend.box.background = element_rect(fill = "white", color = NA), 
          legend.margin = margin(6, 6, 6, 6),
          legend.key = element_rect(fill = "white", color = NA),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 18)
  ) +
  coord_fixed(xlim = c(400000, 800000), ylim = c(6.95E6, 7.5E6))


# ggsave2("{folder_fig}/07b_labelmap_without_labels.svg", gg1, width = 8, height = 12)
# Not used


# Add labels  
gg2 <- gg1 +
  geom_text(
    data = df_stations, 
    aes(x = x + 5000, label = Shortname), hjust = 0, color = "blue3")
  )

ggsave2("{folder_fig}/07b_labelmap_with_labels_to_right.svg", gg2, 
        width = 8, height = 12)

# file manually edited in Inkscape and saved as 07b_labelmap_with_labels_to_right.svg
# 

```
#### Adjust labels in Inkscape  

* Open the result in Inkscape for editing  
    - Start by saving as '07b_labelmap_with_labels_adjusted.svg'  
    - When you open the figure, all objects are grouped; select Object:Ungroup  
    - Now labels can be moved manually  
    - Mouse wheel to move up/down, shift + mouse wheel to move left/right  
    - To edit text, use Text Tool (use arrow tool to resize object if needed)  
    - To add lines, use Bezier and Straight lines tool (left click for each end, right click for finishing). Use shift + click on the colors on the bottom to change line color  
* When finished editing, set background to white   
    - File : Document properties   
    - On the "Page" tab, find Background at the bottom  
    - click "Background color"  
    - Set O (opacity) to 100   
* Make png  
    - File : Export PNG Image  
    - Select "Page" in the top of the menu  
    - Check filename and click Export  
    

## 5. Same plot as 4, Strahler 6      

#### Make a ggplot without labels and save as svg   

* Save map without labels, then copy/paste labels from previous svg map   

    - Select labels using Edit : Select same : Object type  
    - Copy  
    - Paste using Edit : Paste in place  

```{r, fig.width=8, fig.height=10}

gg_back_simp +
  theme(panel.grid.major.x = )

gg1 <- gg_back_simp +
  geom_path(data = df_rivers_strahler6, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol) +
  geom_point(
    data = df_stations, 
    aes(shape = Stasjonstype, fill = Stasjonstype), size = rel(2)) +
  scale_fill_brewer(palette = "Set1") +
  scale_shape_manual(values = c(21,22,24)) +
  theme(  legend.position = c(.05, .95),
          legend.justification = c("left", "top"),
          legend.box.just = "left",
          legend.box.background = element_rect(fill = "white", color = NA), 
          legend.margin = margin(6, 6, 6, 6),
          legend.key = element_rect(fill = "white", color = NA),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 18)
  ) +
  coord_fixed(xlim = c(400000, 800000), ylim = c(6.95E6, 7.5E6))


# ggsave2("{folder_fig}/07b_labelmap_without_labels.svg", gg1, width = 8, height = 12)
# Not used

ggsave2("{folder_fig}/07b_labelmap_strahler6_without_labels.svg", 
        gg1, width = 8, height = 12)

# No need to add and adjust labels - we already did that above  
# 
  geom_text(
    data = df_stations, 
    aes(x = x + 5000, label = Shortname), hjust = 0, color = "blue3")

# file manually edited in Inkscape and saved as 07b_labelmap_with_labels_to_right.svg
# 

```

## 6. Test inset    
  
* __Not used!__   

### a. Define box_corners and box_polygons  

* code from 4a in last year's script  

```{r}

# Define list 
box_corners <- list()

# Inset 1 (the only one)
box_corners[[1]] <- list(x = x_lim, y = y_lim)

# from corners, make data set with 4 lines, one from each corner (anticlockwise from lower left)  
corners_to_polygons <- function(df)
  tibble(x = c(df$x[1], df$x[2], df$x[2], df$x[1]), y = c(df$y[1], df$y[1], df$y[2], df$y[2]))

# Data frame of polygons (UTM coordinates)
box_polygons <- box_corners %>%
  purrr::map_dfr(corners_to_polygons, .id = "boxnumber")

```

### b. Define data_box  

```{r}

pick_data <- function(i, data){
  data %>%
    filter(point_inside(., box_corners[[i]]$x, box_corners[[i]]$y))
}

# test
# pick_data(1, df_stations_all)

# For all boxes  
data_box <- lapply(
  seq_along(box_corners),
  pick_data,
  data = df_stations_all)

```

### c. Define list 
```{r}

gg_box_full <- list()         # full map with rivers and lakes
gg_box_simp <- list()   # coastline only  

```


### d. Inset 1, draft  

* Use only coastline map (not rivers + lakes) so waiting times are shorter  
```{r}

i <- 1
gg1 <- gg_back_simp +
  coord_fixed(xlim = box_corners[[i]]$x, ylim = box_corners[[i]]$y)

if (FALSE){
  # May use interactive graphi in the start, as labels can be hard to see 
  library(ggiraph)
  gg2_interactive <- gg1 + 
    geom_point_interactive(
      data = data_box[[i]], 
      aes(tooltip = Shortname, shape = Stasjonstype, fill = Stasjonstype), size = rel(2))
  girafe(ggobj = gg2_interactive)
}

# Adjust 
df_labs <- data_box[[i]] %>%
  mutate(
    xend = case_when(
      substr(Shortname, 1, 2) == "06" ~ x,
      TRUE ~ x + 3000),
    yend = case_when(
      substr(Shortname, 1, 2) == "12" ~ y + 7000,
      substr(Shortname, 1, 2) == "11" ~ y + 4500,
      substr(Shortname, 1, 2) == "10" ~ y + 3000,
      substr(Shortname, 1, 2) == "06" ~ y - 3000,
      TRUE ~ y),
    # Horizontal adjustment of text: Use 0 for labels under/over point, 
    #   -0.1 for labels to the right, and 1.1 for labels to the left  
    # Effect: makes a little distance between end of line and label text
    hjust = case_when(
      substr(Shortname, 1, 2) == "06" ~ 0,
      TRUE ~ -0.1),
    # Vertical adjustment of text: Use 1.2 for labels under point, 
    #   -0.2 for those over, and 0.5 for those to left/right  
    # Effect: makes a little distance between end of line and label text
    vjust = case_when(
      substr(Shortname, 1, 2) == "06" ~ 1.2,
      TRUE ~ 0.5)
  )

gg2 <- gg1 + 
  geom_point(
    data = data_box[[i]], 
    aes(shape = Stasjonstype, fill = Stasjonstype), size = rel(2))

gg <- gg2 + 
  geom_segment(
    data = df_labs, 
    aes(xend = xend, yend = yend), color = "red") +
  geom_point(
    data = data_box[[i]], 
    aes(shape = Stasjonstype, fill = Stasjonstype), size = rel(2)) +
  geom_text(data = df_labs, 
    aes(x = xend, y = yend, label = Shortname, hjust = hjust, vjust = vjust), 
    color = "red", size = rel(3))

gg

```

### e. Inset 1, finished     

* Use only coastline map (not rivers + lakes) so waiting times are shorter  
```{r}

# i = box_number
# global: df_lakes
make_gg_box <- function(box_number, gg_background, data_river){
  gg_background +
  geom_path(data = data_river, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol) +
  geom_segment(
    data = df_labs, 
    aes(xend = xend, yend = yend), color = "red") +
  geom_point(
    data = data_box[[box_number]], 
    aes(shape = Stasjonstype, fill = Stasjonstype), size = rel(2)) +
  geom_text(data = df_labs, 
    aes(x = xend, y = yend, label = Shortname, hjust = hjust, vjust = vjust), 
    color = "red", size = rel(3)) +
  coord_fixed(xlim = box_corners[[box_number]]$x, 
              ylim = box_corners[[box_number]]$y)

}

gg_box_simp[[i]] <- make_gg_box(i, gg_back_simp, df_rivers_strahler7)
gg_box_full[[i]] <- make_gg_box(i, gg_back_full, df_rivers_strahler5)

gg_box_simp[[i]] 

```


### f. Plot with exported label placement  

```{r, fig.width=8, fig.height=10}

df_labels <- read.csv("Data_input/2022/Referanseelver_labels_2021_v2.csv")

df_labels <- df_labels %>%
  mutate(
    adjustment_h = case_when(
        grepl("ORK", lab) ~ 1,
        TRUE ~ 0),
    lab_x_adj = case_when(
        grepl("ORK", lab) ~ lab_x -13000,
        TRUE ~ lab_x + 13000)
  )
  
df_stations         <- df_stations_all %>%
  left_join(df_labels, by = c("Shortname" = "lab"))

gg1 <- gg_back_simp +
  geom_point(
    data = df_stations, 
    aes(label = Shortname, shape = Stasjonstype)) +
  geom_text(data = df_labels, aes(x = lab_x_adj, y = lab_y, label = lab,
                                  hadj = adjustment_h), 
            color = "red", size = rel(3)) +
  theme(  legend.position = c(.05, .95),
          legend.justification = c("left", "top"),
          legend.box.just = "left",
          legend.box.background = element_rect(fill = "white", color = NA), 
          legend.margin = margin(6, 6, 6, 6),
          legend.key = element_rect(fill = "white", color = NA),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 18)
  ) 

if (save_plots)
  ggsave2("{folder_fig}/07b_labelmap_test.png", gg1, width = 8, height = 12)

gg1


```