---
title: "07 Figures 2018 - maps and barplots"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true

---

Overview maps (types of stations) for Methods chapter (section 3)  
* using UTM zone 32V as projection  
* Data for 7c are saved in 4c   
* "Lange tidsserier" ('long time-series' stations) are used for Methods map, not in Results  

## Overview of process:    
1. Packages and load scripts      
2. Data, includes    
    - station data  
    - background map (coast- + county lines)  
    - rivers  
    - the last two: downloaded as shape (UTM33), but coordinares extracted and converted to UTM32  
3. Defines inset map boxes using a leaflet map; therefore boxes are defined using lat/long  
    - boxes are saved as a list, each of which defining bottom left and top right corner   
4. Prepare data sets in UTM32  
    - station data   
    - box_corners (used to make the inset plots, 'make_subplot_nolabels', and to filter stations for these)
    - box_polygons (used to plot inset rectangles on the big map, 6b)  
5. Is used only as a fast way to make a draft map with labels (used as help for 6a)
6. Build gg3a plot
    - Build gg2_points plot based on background map (gg_back + rivers) + labels, group by group  
    - gg3a map = gg2_points map plus boxes   
7. Functions for making insets  
8. Make insets including labels. the resukt is a list of ggplot objects)
9. Make final plot by adding legend (gg3b), then plot gg3b plus each of the insets   
    - position of insets is quite a bit try and error   

## Overview of some important objects and where they are created      

Box coordinates:    
- 3a2: boxlist, with lat-lon("manually" made by testing leaf2 in 3-c)  
- 4b: 'boxlist' -> 'box_polygons' (UTM coordinates + dimensions)
- 6b: box_polygons -> box_letter_pos   
  
ggplots (gg):  
- 6a: gg_back -> gg2 (adding points and labels outside boxes)
- 6b: gg2 -> gg3a (adding boxes and letters)   
- 8: gg_back + df_stations -> gg_box 1-4 (adding rivers, points, labels)
- 9b: 
    - gg3a -> gg3b (removing legend)  
    - gg3b + gg_box -> gg4 (adding inset maps) 

data:  
- 2a1: df_stations_all (read)
- 2a3: df_stations_all -> df_stations (So. Norway only)  
- 4a: df_stations -> df_stations (adding UTM coordinates)
- 5a: df_stations + boxlist -> df_stations_outside (only used for test plots)  
  
Plots are combined and written to file in a separate script:   
`07b_Figures_2020_labelmap_combine.R`  


## 1. Prerequisites  

### a. Whether and where to save figures  
```{r}
#
# Save figures to file, or just show them in this report?
#
# NOTE: we now use a separate R file (see 9b in this script) 
# - `07b_Figures_2020_labelmap_combine.R`  
#
# save_plots <- TRUE
save_plots <- FALSE


#
# Where to save figures
#
folder_fig <- "Figures/2023_main"

if (!dir.exists(folder_fig))
  dir.create(folder_fig)

```

### b. Packages + map  
```{r}

library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(mapdata)
library(readxl)

# map_norway <- map_data("world", "Norway")
# map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

# Long/lat map (including the smaller islands) - lacking Mjøsa, though! 
#   (and including some North Finnish lakes?)
load("Data_input/Norway_coastline_longlat2.RData")
# rename
map_norway_h <- norway_coast_longlat2
rm(norway_coast_longlat)

# Test plot
# ggplot(map_norway_h) + geom_path(aes(long, lat, group = group))

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()
library(sp)         # SpatialPoints(), CRS(), spTransform()
library(sf)         # st_read
library(ggimage)    # geom_subview(), theme_transparent()

library(glue)       # used in ggplot2() function
library(leaflet)

library(cowplot)

library(scatterD3)  # used to position labels  

source("07_Figures_functions.R")

# Define crs strings for conversion between long/lat and UTM
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"  # note: zone 32

```


## 2. Data

### a1. Data   
* From excel  
```{r, warning=FALSE}

# df_stations_all_OLD <- readRDS("Data/2021/07a_df_stations_2020.rds")
# str(df_stations_all_OLD)

df_stations_all <- readRDS("Data/2023/07a_df_stations_2023.rds")


if (FALSE){
  
  # For reading from excel 
  coltypes <- c("text", "numeric", "numeric", "numeric", "text")
  df_stations_all <- read_excel("Data_input/2022/KartOgFigurgrunnlag2021.xlsx", 
                                range = "A1:E34", 
                                col_types = coltypes) %>%
    rename(Shortname = Rapportnavn,
           Lat = Biologi_Lat,
           Long = Biologi_Long)

  str(df_stations_all)
  
}



```

### a2. Stations, add UTM coordinates
```{r}

# The default transformation for 'add_transformed_coord' is from latlong to 
df_stations_all <- add_transformed_coord(df_stations_all, 
                                     name_x = "Long", name_y = "Lat",
                                     from = "longlat", to = "utm", to_zone = 32)  

write_csv(df_stations_all %>% select(-Stasjonstype),
          "Data_input/2022/KartOgFigurgrunnlag2021.csv")  

# write_csv(very_simple_map %>% add_transformed_coord(),
#           "Data_input/2022/very_simple_map.csv")

```

### a3. Plot all stations  
```{r}

df_stations_all$Stasjonstype %>% table()

very_simple_map <- map_data("world", "Norway")

ggplot(df_stations_all, aes(Long, Lat, color = Stasjonstype)) +
  annotation_map(very_simple_map, fill = "lightgreen") +
  geom_point() +
  # geom_text_repel() +
  coord_map("lambert", 15, 65)  


```

### a4. Split into North and South Norway    

```{r}

df_stations_south <- df_stations_all %>%
  filter(Lat < 65)

df_stations_north <- df_stations_all %>%
  filter(Lat >= 65)

if (TRUE){
  
  ggplot(df_stations_south, aes(Long, Lat, color = Stasjonstype)) +
    annotation_map(very_simple_map, fill = "lightgreen") +
    geom_point() +
    # geom_text_repel() +
    coord_map("lambert", 15, 65) 
  
  ggplot(df_stations_north, aes(Long, Lat, color = Stasjonstype)) +
    annotation_map(very_simple_map, fill = "lightgreen") +
    geom_point() +
    # geom_text_repel() +
    coord_map("lambert", 15, 65) 
  
}

```


### b1. Map with counties (fylke)   

* 
```{r}
# 
# Gotten from Geonorge ("Norske fylker og kommuner illustrasjonsdata 2019 (klippet etter kyst)")
#   https://kartkatalog.geonorge.no/metadata/cb02ab77-d3e6-4500-8a92-ea67367e7734 
#   https://nedlasting.geonorge.no/geonorge/Generell/AdmEnh_klippet_etter_kyst2019.zip  
map_counties_utm33 <- sf::st_read("Data_input/2021_map/fylker2021.json")
# UTM zone 33
# plot(map_counties_utm)

```

### b2. Make simplified coastline  
* Using 'st_simplify'  
    - reduces size from 17 MB to 0.6 MB  
    - see https://www.r-bloggers.com/2021/03/simplifying-geospatial-features-in-r-with-sf-and-rmapshaper/   
    - The simplification changes the geometry column from MULTIPOLYGON to GEOMETRY,
    we must change it back (otherwise `st_coordinates`doesn't work)  
    - See https://cran.r-project.org/web/packages/sf/vignettes/sf3.html  

```{r}

map_counties_utm33_simple <- st_simplify(map_counties_utm33,
                                         preserveTopology = FALSE, dTolerance = 500)

# The simplification () changes the geometry column from to GEOMEtry
# Check:
# class(map_counties_utm33$geometry)         # "sfc_MULTIPOLYGON" "sfc"
# class(map_counties_utm33_simple$geometry)  # "sfc_GEOMETRY" "sfc"
# We change it back like this: 
#  (ref: https://cran.r-project.org/web/packages/sf/vignettes/sf3.html)

map_counties_utm33_simple$geometry <- st_cast(
  map_counties_utm33_simple$geometry, "MULTIPOLYGON")

```

### c. Get coordinates of county map (df_counties_all)  
Used to make the background map  
* We convert the map from UTM zone 33 to UTM 32, as this is more fitting for Southern Norway   (https://upload.wikimedia.org/wikipedia/commons/9/9e/LA2-Europe-UTM-zones.png)
```{r}

map_to_dataframe <- function(map_object){
  st_coordinates(map_object) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2, id = L3)
}

# Extract coordinates and Transform from UTM33 to UTM32
df_counties_all <- map_to_dataframe(map_counties_utm33)
df_counties_all_simple <- map_to_dataframe(map_counties_utm33_simple)

nrow(df_counties_all)
nrow(df_counties_all_simple)
# [1] 798273
# [1] 20095
```



### d. Make background map (gg1_back)    
```{r}

# Check counties: it turns out that 5 = Nordland, 10 = Troms + Finnmark

if (FALSE){
  df_counties_all %>% 
    filter(L1 == 1) %>%
    group_by(id) %>%
    summarise(across(, mean)) %>%
    arrange(y) %>%
    ggplot(aes(x, y, label = id)) +
    geom_text() +
    coord_equal(ratio = 0.5) 
}

# Keep these 4 counties (Trøndelag + Nordland)
# - for both full and simple version
df_counties_full <- df_counties_all %>%
  filter(id %in% c(9,5,6,11))
df_counties_simp_mid <- df_counties_all_simple %>%
  filter(id %in% c(9,5,6,11))
# south Norway
df_counties_simp_so <- df_counties_all_simple %>%
  filter(id %in% c(3,8,11,1,2,4,7))
# north Norway
df_counties_simp_no <- df_counties_all_simple %>%
  filter(id %in% c(5,10))


# Get remaining county numbers
# county_numbers <- unique(df_counties_simp$id)

# Make gg 

gg_from_counties_coastline <- function(mapdata){
  
  result <- ggplot(data = mapdata, aes(x, y)) + 
    geom_blank() + 
    coord_fixed() +
    theme_minimal() +
    theme(panel.grid = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
    )
  
  # Add one county after the other
  county_numbers <- unique(mapdata$id)
  for (i in county_numbers){
    result <- result + 
      geom_polygon(data = mapdata %>% filter(L1 == 1 & id %in% i), 
                   aes(x, y, group = group), fill = "navajowhite", color = "grey30")
  }
  
  invisible(result)
  
}

# Start 'gg_back_full'
gg_back_full <- gg_from_counties_coastline(df_counties_full)
gg_back_simp <- gg_from_counties_coastline(df_counties_all_simple)
gg_back_simp_so <- gg_from_counties_coastline(df_counties_simp_so)
gg_back_simp_no <- gg_from_counties_coastline(df_counties_simp_no)

# test use of ggdata
if (FALSE)
  gg_back_simp + ylim(range(ggdata$y) + c(-100E3, 0))

```

### e1. Rivers

```{r}

# OLD (from shape)
# nc_rivers_strahler4_full <- st_read(
#   "K:\\Kart\\ELVIS\\Hovedelv\\elvis_hovedelv.shp",
#   query = "SELECT * FROM elvis_hovedelv WHERE STRAHLER >= 4")  # only big rivers; saves a little time
#  UTM zone 33

# NEW (geojson)
nc_rivers_full <- st_read(
  "../../Mapdata/NVE_ELVIS_elvenett/NVEData/Elv_Hovedelv.geojson")
str(nc_rivers_full)
table(addNA(nc_rivers_full$nivaa))

# Test: glomma
# nc_test <- nc_rivers_full %>% filter(grepl("Glomma", elvenavn))
# ggplot(nc_test) + geom_sf()

nc_rivers_nivaa3_full <- nc_rivers_full %>%
  filter(nivaa %in% c("1a", "2a", "3a"))
nc_rivers_nivaa2_full <- nc_rivers_full %>%
  filter(nivaa %in% c("1a", "2a"))

# test
# ggplot(nc_rivers_nivaa2_full) + geom_sf()


# Extract coordinates and Transform from UTM33 to UTM32
df_rivers <- nc_rivers_nivaa2_full %>%
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "longlat", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000)  # Fix errors (i.e. remove extremely long segments)

range(df_counties_full$y)
south_limit <- min(df_counties_full$y) - 300000 # 300 km S and N of limits
north_limit <- max(df_counties_full$y) + 300000

# Remove data for North Norway (filter doesn't work, as some data are reshuffeled)
# sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y < south_limit  
# df_rivers_strahler5[sel, c("x","y")] <- NA
# sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y > north_limit  
# df_rivers_strahler5[sel, c("x","y")] <- NA
# 
# sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y < south_limit
# df_rivers_strahler7[sel, c("x","y")] <- NA
# sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y > north_limit
# df_rivers_strahler7[sel, c("x","y")] <- NA

rivercol <- "lightskyblue"

```

### e2 Plot rivers  
```{r}

if (TRUE){
  
  # Test plot
  gg_back_simp +
    geom_path(data = df_rivers, aes(x, y, group = group), col = "red") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))
}
  
if (FALSE){

  gg_back_simp +
    geom_path(data = df_rivers_strahler6_full, aes(x, y, group = group), col = "red") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))

}

```

### f1. Lakes  

```{r}

fn <- "../../Mapdata/Basisdata_0000_Norge_25833_N1000Kartdata_GML/Basisdata_0000_Norge_25833_N1000Arealdekke_GML.gml"
st_layers(fn)
nc_lakes_all <- st_read(fn, layer = "Innsjø")
nc_lakes_all$area <- st_area(nc_lakes_all)
range(nc_lakes_all$area)
# hist(nc_lakes_all$area, breaks = seq(0,400,5)*1E6)

# Keep only the 50% largest lakes
min <- quantile(nc_lakes_all$area, 0.5)
nc_lakes <- nc_lakes_all %>%
  filter(area > min)

# test
# ggplot(nc_lakes) + geom_sf(fill = "lightblue")

data_lakes <- nc_lakes %>%
  # filter(AREA > 40E6) %>%
  # st_transform(crs = "+proj=longlat +ellps=WGS84") %>%  # transform from UTM to long-lat
  st_coordinates() %>%                                  # get coordinates only
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2)

```


### f2. test plot
```{r}


if (TRUE){
  
  table(data_lakes$L1)
  table(data_lakes$L2)
  
  gg_back_simp +
    geom_path(data = df_rivers, aes(x, y, group = group), col = "red") +
    geom_polygon(data = data_lakes, aes(x, y, group = group), fill = "purple")
    # coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
    #             ylim = c(72E5 + c(-1E5,1E5)))
}

```
## Plot with stations

### Select x,y ranges for maps  

```{r}

# Adjust the ranges using the grid in the map

# Northern Norway
lims1_x <- c(0.85E6, 1.35E6)
lims1_y <- c(7.65E6, 8E6)

# Southern Norway
lims2_x <- c(0.25E6, 0.67E6)
lims2_y <- c(6.42E6, 6.88E6)

  gg_back_simp +
    geom_point(data = df_stations_all, aes(x, y)) +
    # coord_fixed(xlim = c(6E5 + c(-1E5,1E5)), 
    #             ylim = c(65E5 + c(-1E5,1E5)))
  scale_x_continuous(breaks = seq(0.2E6, 1.3E6, by = 0.1E6), 
                     minor_breaks = seq(0.2E6, 1.3E6, by = 0.05E6)) +
  scale_y_continuous(breaks = seq(6.4E6, 8E6, by = 0.1E6), 
                     minor_breaks = seq(6.4E6, 8E6, by = 0.05E6)) +
  theme(panel.grid.major = element_line(size = 1),
        panel.grid.minor = element_line(size = 0.5)) +
  annotate("rect", 
           xmin = lims1_x[1], xmax = lims1_x[2], 
           ymin = lims1_y[1], ymax = lims1_y[2], fill = NA, color = "red", size = 1) +
  annotate("rect", 
           xmin = lims2_x[1], xmax = lims2_x[2], 
           ymin = lims2_y[1], ymax = lims2_y[2], fill = NA, color = "red", size = 1)

```

## Final maps  

* Using ggrepel  
* Post-processing in Inkscape (moving labels and making some new lines)  


#### Map 1 - Norhtern Norway  

```{r}

gg1 <- gg_back_simp +
  geom_path(data = df_rivers, aes(x, y, group = group), col = rivercol) +
  geom_polygon(data = data_lakes, aes(x, y, group = group), fill = rivercol) +
  geom_point(data = df_stations_all, aes(x, y)) +
  geom_text_repel(
    data = df_stations_north, 
    aes(label = Shortname, shape = Stasjonstype), color = "blue3", 
    hjust = 0, force = 1, force_pull = 0.4, nudge_x = 20000, box_padding = 0.5,
    point_padding = 0.5) +
  coord_fixed(xlim = lims1_x, ylim = lims1_y)

# gg1 
ggsave(glue("{folder_fig}/07b_labelmap_area1.svg"))
# ggsave("{folder_fig}/07b_labelmap_area1.svg", gg1, width = 8, height = 12)

```

#### Map 2  

```{r}

# df_stations_north -> df_stations_south
# lims1_x, lims1_y -> lims2_x, lims2_y

gg <- gg_back_simp +
  geom_path(data = df_rivers, aes(x, y, group = group), col = rivercol) +
  geom_polygon(data = data_lakes, aes(x, y, group = group), fill = rivercol) +
  geom_point(data = df_stations_all, aes(x, y)) +
  geom_text_repel(
    data = df_stations_south, 
    aes(label = Shortname, shape = Stasjonstype), color = "blue3", 
    hjust = 0, force = 1, force_pull = 0.4, nudge_x = 20000, box_padding = 0.5,
    point_padding = 0.5) +
  coord_fixed(xlim = lims2_x, ylim = lims2_y)

# gg 
ggsave(glue("{folder_fig}/07b_labelmap_area2.svg"), gg)
# ggsave("{folder_fig}/07b_labelmap_area1.svg", gg1, width = 8, height = 12)

```
## Save for script c  

```{r}

saveRDS(gg_back_simp, "Data/backgroundmap2023_gg_back_simp.rds")
saveRDS(df_rivers, "Data/backgroundmap2023_df_rivers.rds")
saveRDS(data_lakes, "Data/backgroundmap2023_data_lakes.rds")

```

