---
title: "Untitled"
author: "DHJ"
date: "23 10 2020"
output: html_document
---


Overview maps (types of stations) for Methods chapter (section 3)  
- using UTM 
* "Lange tidsserier" ('long time-series' stations) are used for Methods map, not in Results  

## 1. Prerequisites  

### a. Whether and where to save figures  
```{r}
#
# SAve figures to file, or just show them in this report?
#
#
save_plots <- TRUE
save_plots <- FALSE


#
# Where to save figures
#
folder_fig <- "Figures/2020"


```

### b. Libs + map  
```{r}
library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(readxl)

# map_norway <- map_data("world", "Norway")
# map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

# Long/lat map (including the smaller islands) - lacking Mjøsa, though! 
#   (and including some North Finnish lakes?)
load("Data_input/Norway_coastline_longlat2.RData")
# rename
map_norway_h <- norway_coast_longlat2
rm(norway_coast_longlat)

# Test plot
# ggplot(map_norway_h) + geom_path(aes(long, lat, group = group))

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()
library(sp)         # SpatialPoints(), CRS(), spTransform()
library(sf)         # st_read
library(ggimage)    # geom_subview(), theme_transparent()

library(glue)       # used in ggplot2() function
library(leaflet)

library(cowplot)

source("07_Figures_functions.R")

# Define crs strings for conversion between long/lat and UTM
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"

```
### c. Define colours for classes  
```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no

```

## 2. Data   

### a. Data from script 7a and 7b  
```{r}

# From script 7a
df_index <- readRDS("Data/2020/07a_df_index_2019.rds")

# From script 7b, part 4c
df_stations <- readRDS("Data/2020/07b_df_stations.rds")   # with UTM 32 coordinates
box_dim <- readRDS("Data/2020/07b_box_dim.rds")
box_polygons <- readRDS("Data/2020/07b_box_polygons.rds")

```

### b. Map with counties (fylke)  
```{r}

# Code same as in script 7b

# Gotten from Geonorge ("Norske fylker og kommuner illustrasjonsdata 2019 (klippet etter kyst)")
#   https://kartkatalog.geonorge.no/metadata/cb02ab77-d3e6-4500-8a92-ea67367e7734 
#   https://nedlasting.geonorge.no/geonorge/Generell/AdmEnh_klippet_etter_kyst2019.zip  
map_counties_utm33 <- sf::st_read("Data_input/2019/AdmEnh_klippet_etter_kyst2019/Fylker19.geojson")
# UTM zone 33

# Get coordinates of county map (df_counties)  
# We convert corodinates from UTM zone 33 to UTM 32, as this is more fitting for Southern Norway   
# Extract coordinates and Transform from UTM33 to UTM32
df_counties <- st_coordinates(map_counties_utm33) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2, id = L3)

```

### c. Make background map (gg_back)    
```{r}

# Code same as in script 7b

# Counties: 11 = Nordland, 3 = Troms, 2 = Finnmark (see 7b)
# Remove these 3 counties
df_counties <- df_counties %>%
  filter(!id %in% c(11,3,2))

# Get remaining county numbers
county_numbers <- unique(df_counties$id)

# Start 'gg_back'
gg_back <- ggplot(data = df_counties, aes(x, y)) + 
  geom_blank() + 
  coord_fixed() +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        )

# Add one county after the other
for (i in county_numbers){
  gg_back <- gg_back + 
    geom_polygon(data = df_counties %>% filter(L1 == 1 & id %in% i), 
                 aes(x, y, group = group), fill = "navajowhite", color = "grey30")
}

# For adjusting limits:
ggdata <- layer_data(gg_back)

```


## 3. Make pies  

### a. Start making 'df_pies'  
Also writes df_stations_vf to excel (later manipulated semi-manually and used in part 6)   
```{r}

# Start with location data on Vannforekomst-level
df_pies <- df_stations

```


### b. Ecological class, levels and colors    
```{r}

# df_colors$Status_no
# class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

df_pies <- df_pies %>%
  mutate(
    Class_ecol = case_when(
      is.na(Index_ecol) ~ "Uklassifisert",
      Index_ecol < 0.2 ~ "Svært dårlig", 
      Index_ecol < 0.4 ~ "Dårlig", 
      Index_ecol < 0.5 ~ "Moderat", 
      Index_ecol < 0.8 ~ "God", 
      Index_ecol <= 1 ~ "Svært god"),
    Class_ecol = factor(Class_ecol, levels = df_colors$Status_no)
  ) %>%
  left_join(
    df_colors %>% select(Status_no, Class_color),
    by = c("Class_ecol" = "Status_no")
  ) %>%
  rename(Colour_ecol = Class_color)  

ggplot(df_pies, aes(Class_ecol, Index_ecol, fill = Class_ecol)) + 
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = class_colors) +
  theme(panel.background = element_rect(fill = "grey70"), panel.grid = element_blank())

```

### c. Chemical class, levels and colors    
```{r}

df_pies <- df_pies %>%
  mutate(
    Colour_chem = case_when(
      is.na(Class_chem) ~ class_colors["Uklassifisert"],
      Class_chem %in% "God" ~ class_colors["Svært god"],
      Class_chem %in% "Ikke god" ~ class_colors["Svært dårlig"],
      Class_chem %in% "i.d." ~ class_colors["Uklassifisert"])
  )



```

### d. Make pies from data frame 'df_pies', and add to 'df_pies'
```{r}      

# Function - make pie for line number i
make_pie_linenumber_indexvalues <- function(i){
  df <- df_pies[i, c("Colour_ecol", "Colour_chem")]
  make_pie_from_colours(as.character(df))
}

# TEST
make_pie_linenumber_indexvalues(1)

# test - should make 3 plots with one pie in each  
if (FALSE){
  grep("GLO1", df_pies$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("GLO3", df_pies$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("ORR1", df_pies$Shortname) %>% make_pie_linenumber_indexvalues()
}

# Make all pies (a list)
pies <- 1:nrow(df_pies) %>% purrr::map(~make_pie_linenumber_indexvalues(.))
length(pies)
# pies[[9]]

# Add pies to dataframe (as a list column)
df_pies$pie = pies

```
```{r}
gg <- gg_back +
  geom_point(data = df_pies[c(1,5,10),], aes(x = x, y = y))
gg

```

## Map outside boxes  

### a. Plot without labels  
```{r}

#
# Width and height of pies
#   
df_pies$width = 20E3    # Sets size of pies
df_pies$height = 20E3   

#
# Make data set for stations outside inset plots
#

df_pies_outside <- df_pies
for (i in unique(box_polygons$boxnumber)){
  box <- box_polygons %>% filter(boxnumber == i)
  df_pies_outside <- df_pies_outside %>%
    filter(
      !(x > min(box$x) & x < max(box$x) & y > min(box$y) & y < max(box$y))
    )
}

gg1 <- gg_back +
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               )
# gg

fn <- glue("{folder_fig}/07_qualitymap_outside_boxes1.png")
scale <- 1.5
ggsave(fn, gg1, width = 18*scale, height = 25*scale, units = "cm", dpi = 500/scale)  

```

### b. Prepare label positions  
```{r}



# Filter using entire Shortname:
group1 <- c("Gruve.O5","Gruve.O4","Gruve.O3","Gruve.Ya")
group2a <- c("GruveF2","Gruve.F4") 
group2b <- c("Gruve.F5","Gruve.F7") 
# Filter using the two first characters (using substr() on Shortname):
group3 <- c("01","03","04") 
group4a <- c("47","50","51") 
group4b <- c("48","49") 
group5 <- c("35","36","37") 
group6a <- c("11","12","13") 
group6b <- c("08","09","10") 



# NOT NEEDED? DELETE?
# get_x <- function(name, data = df_stations)
#   subset(data, Shortname %in% name)$x
# get_y <- function(name, data = df_stations)
#   subset(data, Shortname %in% name)$y

# For setting ylim:
# ggdata <- layer_data(gg_back)

gg2 <- gg_back +
  theme(legend.position = "none") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group3), 
    xdist = 30E3, xadj_start = 7E3,
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group4a), 
    xdist = 40E3, xadj_start = 7E3, y_even_dist = 20E3, y_even_pos = 50E3, 
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group4b), 
    xdist = 50E3, xadj_start = 7E3, y_even_dist = 20E3, y_even_pos = -30E3, 
    order = "E to W",
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group5), 
    xdist = 35E3, xadj_start = 7E3, y_even_dist = 20E3, y_even_pos = -40E3, 
    order = "E to W",
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group6a),
    xdist = 30E3, y_even_dist = 20E3, y_even_pos = -60E3,
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group6b),
    xdist = 30E3, y_even_dist = 20E3, y_even_pos = -60E3,
    color = "blue3", segment.color = "blue3") +
  geom_subview(data = df_pies %>% filter(!Shortname %in% c(group1, group2a, group2b)), 
               aes(x = x, y = y, subview = pie, width = width, height = height)) +
  xlim(range(ggdata$x) + c(-50E3, 50E3)) +  
  ylim(range(ggdata$y) + c(-50E3, 0))

# gg2

fn <- glue("{folder_fig}/07_qualitymap_outside_boxes2.png")
scale <- 1.5
ggsave(fn, gg2, width = 18*scale, height = 25*scale, units = "cm", dpi = 500/scale)  
  

```

### c. Map with inset boxes    
```{r, fig.width=8, fig.height=10}

#
# Make data set for the letters beside the box
#
box_letter_pos <- box_polygons %>%
  group_by(boxnumber) %>%
  summarise(
    x = max(x) + 7E3,  # left of left edge 
    y = max(y))         # top edge (we use vjust to adjust the position)
box_letter_pos$letter <- LETTERS[as.numeric(box_letter_pos$boxnumber)]
box_letter_pos

#
# Add boxes and letters
#
gg3 <- gg2 +
  geom_polygon(data = box_polygons, aes(group = boxnumber),
               fill = NA, colour = "red3", size = rel(1.5)) +
  geom_text(data = box_letter_pos, aes(label = letter), 
            size = rel(8), colour = "red3", hjust = 0, vjust = 1) 

# gg3

```

## Insets  
These plots differ form the 
```{r}

gg_box <- vector("list", length(box_polygons))
data_box <- vector("list", length(box_polygons))

```

### Defining unctions  
```{r}

#
# Function for making 'data_box', which is the data for the pies
#   inside box number 'i'
#
# sizeratio = 0.15 is found by trial and error
#

qualplot_make_data_box <- function(i, polygon, data, sizeratio = 0.15){
  
  data_box[[i]]  <- data %>%
    filter(
      (x > min(polygon$x) & x < max(polygon$x) & 
         y > min(polygon$y) & y < max(polygon$y))
    )
  
  data_box[[i]] %>%
    mutate(width = width*sizeratio,
           height = height*sizeratio)
}


#
# Function for adding pies for box number 'i'
# (which we do *after* adding labels)
#
qualplot_add_pies <- function(gg, data, box, i) {
  
  gg <- gg +
    geom_subview(data = data, 
                 aes(x = x, y = y, subview = pie, width = width, height = height)) +
    annotate("text", label = LETTERS[i], 
             x = min(box$x) + 1200, y = max(box$y) - 1500, 
             size = rel(8), colour = "red3") +
    coord_fixed(xlim = range(box$x), ylim = range(box$y)) +
      theme(legend.position = "none",
            plot.background = element_rect(
              colour = "black",
              size = 1)
            )

}

                                 

```

### Inset 1
```{r, fig.width = 5, fig.height = 5}

#
# For each inset 1-5:
#   - the TOP (except "i <- 1") and BOTTOM parts are always the same
#   - the MIDDLE part between A and B (adding labels) is copy-pasted 
#   from script 07b (yes, I know...)
#

i <- 1

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back

# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("43","46") ~ "left",
    substr(Shortname,1,2) %in% "45" ~ "above",
    TRUE ~ "right"))

# Add levels
gg_box[[i]] <- gg_box[[i]] +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "right"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "left"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "above"),
    xdist = 4E3, same_x = FALSE, xadj_start = 900, 
    y_even_dist = 0, y_even_pos = 3E3,
    color = "blue3", segment.color = "blue3")

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```

### Inset 2
```{r, fig.width = 5, fig.height = 5}

i <- 2

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back

gg_box[[i]] <- gg_box[[i]] +
  geom_text_repel(
      data = data_box[[i]], 
      aes(label = Shortname), color = "blue3", 
      label.padding = 0.15, point.padding = 1)

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```

### Inset 3
```{r, fig.width = 5, fig.height = 5}

i <- 3

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back

# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("19") ~ "left",
    TRUE ~ "right"))

# Add labels  
gg_box[[i]] <- gg_box[[i]] +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "right"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "left"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3")

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```
### Inset 4
```{r, fig.width = 5, fig.height = 5}

i <- 4

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back

# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("18") ~ "rightbelow",
    substr(Shortname,1,2) %in% c("14") ~ "left",
    TRUE ~ "right"))

# Add labels  
gg_box[[i]] <- gg_box[[i]] +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "right"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "left"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "rightbelow"),
    xdist = 4E3, same_x = FALSE, xadj_start = 900, 
    y_even_dist = 0, y_even_pos = -3E3,
    color = "blue3", segment.color = "blue3")

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)



# gg_box[[i]]

```

### Inset 5
```{r, fig.width = 5, fig.height = 5}

i <- 5

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back

# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("07") ~ "right",
    TRUE ~ "left"))

# Add labels  
gg_box[[i]] <- gg_box[[i]] +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "right"),
    xdist = 2E3, same_x = FALSE, xadj_start = 400, 
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "left"),
    xdist = 2E3, same_x = FALSE, xadj_start = 400,  
    color = "blue3", segment.color = "blue3")

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)

# gg_box[[i]]

```

## Final map
```{r}

# Positions on scale 0 to 1 (of lower left corner)
# These are strangely hard to set correctly
box_pos <- tibble::tribble(
  ~x,    ~y,
  0.37,  0.6,
  0.07,  0.6,
  0.07,  0.44,  # 
  0.07,  0.15,
  0.70,  0.15
)

# Size, given on scale 0 to 1 
# box_dim$x[2] = 0.3 in size:
box_dim$x_scale = box_dim$x/box_dim$x[2]*0.3
box_dim$y_scale = box_dim$y/box_dim$x[2]*0.3

gg4 <- ggdraw() +
  draw_plot(gg3, x = 0.15, y = 0, scale = 0.7)
for (i in 1:5){
  gg4 <- gg4 + draw_plot(
    gg_box[[i]], 
    x = box_pos$x[i], y = box_pos$y[i], 
    width = box_dim$x_scale[i], height = box_dim$y_scale[i]
    )
  }

fn <- glue("{folder_fig}/07_qualitymap_complete.png")
scale <- 1.5
ggsave(fn, gg4, width = 18*scale, height = 25*scale, units = "cm", dpi = 500/scale)  

```


```{r}


```


