---
title: "Untitled"
author: "DHJ"
date: "May 2023"
output: html_document
---


"Quality maps" showing one pie per station for Results chapter     
* Pie: color of left half shows ecological quality, colour of right half chemical quality  
  
## Code overview   
* 2a: loads data (in 2021, also inset map coordinates)    
* 2b-d: County map data is built up from scratch, as in script 7b   
* 3.  
    - Makes pie ggplot objects using the functions make_pie() and make_pie_from_colours()   
    - These are stored in the column 'pie' in th data frame 'df_pies'   
* 4. Make main map (all symbols, but labels are outside inset boxes only)   
    - Very similar to script 7b   
    - However, since 7b stores ggplot objects, not position of labels, much code is copy-pasted
    from script 7b   
* 5. Make inset plots   
    - None this year     

## 1. Prerequisites  

### a. Whether and where to save figures  
```{r}
#
# Save figures to file, or just show them in this report?
#

# save_plots <- TRUE
save_plots <- FALSE


#
# Where to save figures
#
folder_fig <- "Figures/2023_main"


```

### b. Libs + map  
```{r}

library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(readxl)

# map_norway <- map_data("world", "Norway")
# map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

# Long/lat map (including the smaller islands) - lacking Mjøsa, though! 
#   (and including some North Finnish lakes?)
load("Data_input/Norway_coastline_longlat2.RData")
# rename
map_norway_h <- norway_coast_longlat2
rm(norway_coast_longlat)

# Test plot
# ggplot(map_norway_h) + geom_path(aes(long, lat, group = group))

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()
library(sp)         # SpatialPoints(), CRS(), spTransform()
library(sf)         # st_read
library(ggimage)    # geom_subview(), theme_transparent()

library(glue)       # used in ggplot2() function
library(leaflet)

library(cowplot)

source("07_Figures_functions.R")

# Define crs strings for conversion between long/lat and UTM
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"

```
### c. Define colours for classes  
```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no



```

## 2. Data   

### a1. Data from script 7a and 7b  
```{r}

# From script 7a
df_index_barplot <- readRDS("Data/2023/07a_df_index_barplot_2023.rds")
df_stations_all <- readRDS("Data/2023/07a_df_stations_2023.rds")

df_stations_all <- add_transformed_coord(df_stations_all, 
                                     name_x = "Long", name_y = "Lat",
                                     from = "longlat", to = "utm", to_zone = 32)  

```


### a2. Plot all stations  

```{r}

ggplot(df_stations_all, aes(Long, Lat)) +
  geom_point() +
  coord_map("lambert", 15, 65)  

```


### a3. Split into North and South Norway    

```{r}

df_stations_south <- df_stations_all %>%
  filter(Lat < 65)

df_stations_north <- df_stations_all %>%
  filter(Lat >= 65)

df_stations_all %>%
  mutate(region = ifelse(Lat >= 65, "North", "South")) %>%
  ggplot(aes(Long, Lat, color = Stasjonstype)) +
  annotation_map(very_simple_map, fill = "lightgreen") +
  geom_point() +
  facet_wrap(vars(region))    # , scales = "free"


```




## 3. Make pies  

### a. Start making 'df_pies'  
Also writes df_stations_vf to excel (later manipulated semi-manually and used in part 6)    
- Note that we use 'df_stations_all', i.e. also include the Northern ones   
```{r}

# Start with location data on Vannforekomst-level
df_pies_all <- df_stations_all %>%
  left_join(df_index_barplot %>% select(Rapportnavn, nEQR_ecol_klasse),
            by = c("Shortname" = "Rapportnavn")) %>%
  rename(Class_ecol = nEQR_ecol_klasse)


```


### b. Ecological class, levels and colors    
```{r}


# df_colors$Status_no
# class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")


df_pies_all <- df_pies_all %>%
  left_join(
    df_colors %>% select(Status_no, Class_color),
    by = c("Class_ecol" = "Status_no")
  ) %>%
  rename(Colour_ecol = Class_color)  

ggplot(df_pies_all, aes(Class_ecol, Index_ecol, fill = Class_ecol)) + 
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = class_colors, drop = FALSE) +
  theme(panel.background = element_rect(fill = "grey70"), panel.grid = element_blank())

```


### c. Chemical class, levels and colors    

```{r}

df_pies_all <- df_pies_all %>%
  mutate(
    Colour_chem = case_when(
      is.na(Class_chem) ~ class_colors["Uklassifisert"],
      Class_chem %in% "God" ~ class_colors["Svært god"],
      Class_chem %in% "Ikke god" ~ class_colors["Svært dårlig"],
      Class_chem %in% c("i.d.", "ID") ~ class_colors["Uklassifisert"])
  )

xtabs(~addNA(Colour_chem) + addNA(Class_chem), df_pies_all)

```


### d. Make pies from data frame 'df_pies_all', and add to 'df_pies_all'  

```{r, fig.width=3, fig.height=3}      

# Function - make pie for line number i
make_pie_linenumber_indexvalues <- function(i){
  df <- df_pies_all[i, c("Colour_ecol", "Colour_chem")]
  make_pie_from_colours(as.character(df))
}

# TEST
make_pie_linenumber_indexvalues(1)
make_pie_linenumber_indexvalues(2)
make_pie_linenumber_indexvalues(3)

# test - should make 3 plots with one pie in each  
if (FALSE){
  grep("03.ORK1", df_pies_all$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("02.ORK2", df_pies_all$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("01.ORK3", df_pies_all$Shortname) %>% make_pie_linenumber_indexvalues()
}

# Make all pies (a list)
pies <- 1:nrow(df_pies_all) %>% purrr::map(~make_pie_linenumber_indexvalues(.))
length(pies)
# check:
# pies[[1]]

# Add pies to dataframe (as a list column)
df_pies_all$pie = pies
# check:
# df_pies_all$pie[1]

# df <- df_pies_all %>% filter(!Shortname %in% c(group1, group2a, group2b))
# df$pie[1]

```

### e. Test  
```{r}

df_pies_test <- df_pies_all[c(1,5,10),]

#
# Width and height of pies
#   
df_pies_test$width = 450E3    # Sets size of pies
df_pies_test$height = 450E3   

gg <- gg_back_simp +
  geom_point(data = df_pies_test, aes(x = x, y = y))
gg

```

## 4. Map   

* We didn't have to make any boxes this time, so this is the entire map     

### a. Test plot    
```{r}

# Pick all pies    
df_pies <- df_pies_all

# For the ones in Southern Norway: use
#   filter(Lat < 65)

#
# Width and height of pies
#   
df_pies$width = 14E3    # Sets size of pies
df_pies$height = 14E3   

#
# Make data set for stations outside inset plots
#

df_pies_outside <- df_pies

#
# All pies are outside so we skip the next part  
#
# for (i in unique(box_polygons$boxnumber)){
#   box <- box_polygons %>% filter(boxnumber == i)
#   df_pies_outside <- df_pies_outside %>%
#     filter(
#       !(x > min(box$x) & x < max(box$x) & y > min(box$y) & y < max(box$y))
#     )
# }

gg1 <- gg_back_simp +
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               )
# gg

if (save_plots){  
  fn <- glue("{folder_fig}/07c_quality_no_rivers_lakes.png")
  scale <- 1.5
  ggsave(fn, gg1, width = 18*scale, height = 25*scale, 
         units = "cm", dpi = 500/scale)  
}

```


### b. Make a ggplot without labels and save as svg   

* Makes quality (cake) figure named 'without_labels' in svg format   
    - Also include points 
* Copied labels from label map and adjusted them  
    - Opened in Inkscape and saved as `07c_quality_strahler6_with_labels_adjusted.svg`  
    - Also opened label map `07b_labelmap_strahler6_with_labels_adjusted.svg` in Inkscape  
    - Select labels using Edit : Select same : Object type  
    - Copy  
    - Paste using Edit : Paste in place   
* Edited label and pie placements in Inkscape   
    - When we had to move a pie, we added a line (width 1.5) between the point and the pie (see final figure)   
* Add legend  
    - Colors and text, see below (part c)  
    - the small circle copied from`Qualitymap_2021_legend.svg`   
* Set background to white and export to `.png` (see tips in script 07b part 4)   

    
```{r, fig.width=8, fig.height=10}

# Northern Norway
lims1_x <- c(0.85E6, 1.35E6)
lims1_y <- c(7.65E6, 8E6)

# Southern Norway
lims2_x <- c(0.25E6, 0.67E6)
lims2_y <- c(6.42E6, 6.88E6)

gg1 <- gg_back_simp +
  geom_path(data = df_rivers,
            aes(group = group), col = rivercol) +
  geom_polygon(data = data_lakes,
               aes(group = group), col = rivercol, fill = rivercol) +
  # Add points - normally covered by the pies, but are used if we have to move overlapping pies in Inkscape
  # - see final file '07c_quality_strahler6_with_labels_adjusted'  
  geom_point(data = df_pies_outside, 
             shape = 15, size = rel(1)) +
  # Add pies  
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               ) +
  geom_text(data = df_pies_outside, aes(label = Shortname), hjust = 0, vjust = 0.5, nudge_x = 10000) +
  # Extent exactly the same as for 7b map ("labelmap")  
  # - this facilitates copy-paste of labels  
  coord_fixed(xlim = lims1_x, ylim = lims1_y)


# ggsave2("{folder_fig}/07b_labelmap_without_labels.svg", gg1, width = 8, height = 12)
# Not used

# gg1

ggsave(glue("{folder_fig}/07c_quality_map1_fromscript.svg"), gg1)

```
```{r, fig.width=8, fig.height=10}

# Southern Norway
# lims1_x, lims1_y -> lims2_x, lims2_y
# file name: 07c_quality_map1 -> 07c_quality_map2

gg1 <- gg_back_simp +
  geom_path(data = df_rivers,
            aes(group = group), col = rivercol) +
  geom_polygon(data = data_lakes,
               aes(group = group), col = rivercol, fill = rivercol) +
  # Add points - normally covered by the pies, but are used if we have to move overlapping pies in Inkscape
  # - see final file '07c_quality_strahler6_with_labels_adjusted'  
  geom_point(data = df_pies_outside, 
             shape = 15, size = rel(1)) +
  # Add pies  
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               ) +
  geom_text(data = df_pies_outside, aes(label = Shortname), hjust = 0, vjust = 0.5, nudge_x = 10000) +
  # Extent exactly the same as for 7b map ("labelmap")  
  # - this facilitates copy-paste of labels  
  coord_fixed(xlim = lims2_x, ylim = lims2_y)


# ggsave2("{folder_fig}/07b_labelmap_without_labels.svg", gg1, width = 8, height = 12)
# Not used

# gg1

ggsave(glue("{folder_fig}/07c_quality_map2_fromscript.svg"), gg1)

```

