---
title: "Untitled"
author: "DHJ"
date: "23 10 2020"
output: html_document
---


"Quality maps" showing one pie per station for Results chapter     
* Pie: color of left half shows ecological quality, colour of right half chemical quality  
  
Code overview   
* 2a: loads inset maps coordinates (box_dim and box_polygon) made in scr. 7b   
* 2b-d: County map is built up from scratch, as in script 7b   
* 3.  
    - Makes pie ggplot objects using the functions make_pie() and make_pie_from_colours()   
    - These are stored in the column 'pie' in th data frame 'df_pies'   
* 4. Make main map (all symbols, but labels are outside inset boxes only)   
    - Very similar to script 7b   
    - However, since 7b stores ggplot objects, not position of labels, much code is copy-pasted
    from script 7b   
* 5. Make inset plots   
    - As 4: much code is copy-pasted from script 7b  

## 1. Prerequisites  

### a. Whether and where to save figures  
```{r}
#
# Save figures to file, or just show them in this report?
#

save_plots <- TRUE
# save_plots <- FALSE


#
# Where to save figures
#
folder_fig <- "Figures/2021_main"


```

### b. Libs + map  
```{r}

library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(readxl)

# map_norway <- map_data("world", "Norway")
# map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

# Long/lat map (including the smaller islands) - lacking Mjøsa, though! 
#   (and including some North Finnish lakes?)
load("Data_input/Norway_coastline_longlat2.RData")
# rename
map_norway_h <- norway_coast_longlat2
rm(norway_coast_longlat)

# Test plot
# ggplot(map_norway_h) + geom_path(aes(long, lat, group = group))

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()
library(sp)         # SpatialPoints(), CRS(), spTransform()
library(sf)         # st_read
library(ggimage)    # geom_subview(), theme_transparent()

library(glue)       # used in ggplot2() function
library(leaflet)

library(cowplot)

source("07_Figures_functions.R")

# Define crs strings for conversion between long/lat and UTM
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"

```
### c. Define colours for classes  
```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no

```

## 2. Data   

### a1. Data from script 7a and 7b  
```{r}

# From script 7a
df_index <- readRDS("Data/2021/07a_df_index_2020.rds")
df_index_barplot <- readRDS("Data/2021/07a_df_index_barplot_2020.rds")

# From script 7b, part 4c
df_stations_all <- readRDS("Data/2021/07b_df_stations.rds")   # with UTM 32 coordinates

box_dim <- readRDS("Data/2021/07b_box_dim.rds")
box_polygons <- readRDS("Data/2021/07b_box_polygons.rds")

```

### a2. Plot all stations  
```{r}

ggplot(df_stations_all, aes(Long, Lat)) +
  geom_point() +
  coord_map("lambert", 15, 65)  

```

### a3. Split into North and South Norway    
- The southern one is called 'df_stations' just to keep with previous work  
```{r}

df_stations <- df_stations_all %>%
  filter(Lat < 65)

df_stations_north <- df_stations_all %>%
  filter(Lat >= 65)

```

### b. Map with counties (fylke)  
```{r}

# Code same as in script 7b

# Gotten from Geonorge ("Norske fylker og kommuner illustrasjonsdata 2021 (klippet etter kyst)")

map_counties_utm33 <- sf::st_read("Data_input/2021_map/fylker2021.json")

# Get coordinates of county map (df_counties)  
# We convert corodinates from UTM zone 33 to UTM 32, as this is more fitting for Southern Norway   
# Extract coordinates and Transform from UTM33 to UTM32
df_counties <- st_coordinates(map_counties_utm33) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2, id = L3)


# Extract coordinates and Transform from UTM33 to UTM32
df_counties_all <- st_coordinates(map_counties_utm33) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2, id = L3)

```

### c. Make background map (gg_back)    
```{r}

# Check counties: it turns out that 5 = Nordland, 10 = Troms + Finnmark
if (FALSE){
  df_counties_all %>% 
    filter(L1 == 1) %>%
    group_by(id) %>%
    summarise(across(, mean)) %>%
    arrange(y) %>%
    ggplot(aes(x, y, label = id)) +
    geom_text()
}

# Remove these 3 counties (Northern Norway)
df_counties <- df_counties_all %>%
  filter(!id %in% c(5,10))

# Get remaining county numbers
county_numbers <- unique(df_counties$id)

# Start 'gg_back'
gg_back <- ggplot(data = df_counties, aes(x, y)) + 
  geom_blank() + 
  coord_fixed() +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        )

# Add one county after the other
for (i in county_numbers){
  gg_back <- gg_back + 
    geom_polygon(data = df_counties %>% filter(L1 == 1 & id %in% i), 
                 aes(x, y, group = group), fill = "navajowhite", color = "grey30")
}

# For adjusting limits:
ggdata <- layer_data(gg_back)

gg_back

# test use of ggdata
if (FALSE)
  gg_back + ylim(range(ggdata$y) + c(-100E3, 0))

```

### d. Rivers

```{r}

nc_rivers_strahler4 <- st_read(
  "K:\\Kart\\ELVIS\\Hovedelv\\elvis_hovedelv.shp",
  query = "SELECT * FROM elvis_hovedelv WHERE STRAHLER >= 4")  # only big rivers; saves a little time
#  UTM zone 33

# Extract coordinates and Transform from UTM33 to UTM32
df_rivers_strahler5 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 5) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000)  # Fix errors (i.e. remove extremely long segments)

df_rivers_strahler6 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 6) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000) # Fix errors (i.e. remove extremely long segments)


df_rivers_strahler7 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 7) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000) # Fix errors (i.e. remove extremely long segments)


north_limit <- 7240000    # number found using ggplotly

# Remove data for North Norway (filter doesn't work, as some data are reshuffeled)
sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y > north_limit  
df_rivers_strahler5[sel, c("x","y")] <- NA

sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y > north_limit
df_rivers_strahler7[sel, c("x","y")] <- NA

rivercol <- "lightskyblue"

if (FALSE){
  # Test plot
  ggplot() +
    geom_path(data = df_rivers_strahler7, aes(x, y, group = group), col = "red") 
}

```

### e. Lakes  

Get coordinates (in zone 32)   
```{r}

nc_lakes <- st_read("K:/Kart/N1000/VANN.shp")
st_crs(nc_lakes) <- "+proj=utm +zone=33"  # set coordinate system

# Extract coordinates and Transform from UTM33 to UTM32
df_lakes <- st_coordinates(nc_lakes) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2)

# Mjøsa only 
df_lakes_mjosa <- df_lakes %>% filter(group == 3462)

```


## 3. Make pies  

### a. Start making 'df_pies'  
Also writes df_stations_vf to excel (later manipulated semi-manually and used in part 6)   
```{r}

# Start with location data on Vannforekomst-level
df_pies <- df_stations %>%
  left_join(df_index_barplot %>% select(Rapportnavn, nEQR_ecol_klasse),
            by = c("Shortname" = "Rapportnavn")) %>%
  rename(Class_ecol = nEQR_ecol_klasse)


```


### b. Ecological class, levels and colors    
```{r}


# df_colors$Status_no
# class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")


df_pies <- df_pies %>%
  left_join(
    df_colors %>% select(Status_no, Class_color),
    by = c("Class_ecol" = "Status_no")
  ) %>%
  rename(Colour_ecol = Class_color)  

ggplot(df_pies, aes(Class_ecol, Index_ecol, fill = Class_ecol)) + 
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = class_colors, drop = FALSE) +
  theme(panel.background = element_rect(fill = "grey70"), panel.grid = element_blank())

```

### c. Chemical class, levels and colors    
```{r}

df_pies <- df_pies %>%
  mutate(
    Colour_chem = case_when(
      is.na(Class_chem) ~ class_colors["Uklassifisert"],
      Class_chem %in% "God" ~ class_colors["Svært god"],
      Class_chem %in% "Ikke god" ~ class_colors["Svært dårlig"],
      Class_chem %in% c("i.d.", "ID") ~ class_colors["Uklassifisert"])
  )



```

### d. Make pies from data frame 'df_pies', and add to 'df_pies'
```{r, fig.width=3, fig.height=3}      

# Function - make pie for line number i
make_pie_linenumber_indexvalues <- function(i){
  df <- df_pies[i, c("Colour_ecol", "Colour_chem")]
  make_pie_from_colours(as.character(df))
}

# TEST
make_pie_linenumber_indexvalues(1)
make_pie_linenumber_indexvalues(2)
make_pie_linenumber_indexvalues(3)

# test - should make 3 plots with one pie in each  
if (FALSE){
  grep("GLO1", df_pies$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("GLO3", df_pies$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("ORR1", df_pies$Shortname) %>% make_pie_linenumber_indexvalues()
}

# Make all pies (a list)
pies <- 1:nrow(df_pies) %>% purrr::map(~make_pie_linenumber_indexvalues(.))
length(pies)
# check:
# pies[[1]]

# Add pies to dataframe (as a list column)
df_pies$pie = pies
# check:
# df_pies$pie[1]

# df <- df_pies %>% filter(!Shortname %in% c(group1, group2a, group2b))
# df$pie[1]

```

### e. Test  
```{r}
gg <- gg_back +
  geom_point(data = df_pies[c(1,5,10),], aes(x = x, y = y))
gg

```

## 4. Map outside boxes  

### a. Plot without labels  
```{r}

#
# Width and height of pies
#   
df_pies$width = 20E3    # Sets size of pies
df_pies$height = 20E3   

#
# Make data set for stations outside inset plots
#

df_pies_outside <- df_pies
for (i in unique(box_polygons$boxnumber)){
  box <- box_polygons %>% filter(boxnumber == i)
  df_pies_outside <- df_pies_outside %>%
    filter(
      !(x > min(box$x) & x < max(box$x) & y > min(box$y) & y < max(box$y))
    )
}

gg1 <- gg_back +
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               )
# gg

if (save_plots){
  fn <- glue("{folder_fig}/07c_qualitymap_outside_boxes1.png")
  scale <- 1.5
  ggsave(fn, gg1, width = 18*scale, height = 25*scale, units = "cm", dpi = 500/scale)  
}

```

### a. Build gg2 plot   
* Includes labels and rivers   
NOTE: The less frustrating way to build this code is to code in an ordinary R script (e.g.,  '07_Figures_2020_testmap.R')   
* Easier to 'try and fail' when the plot is made in a separate window    
* When finished, copy code back to this chunk  
```{r, fig.width=8, fig.height=10}


# Filter using entire Shortname:
group1 <- c("Gruve.O5","Gruve.O4","Gruve.O3","Gruve.Ya")
group2a <- c("GruveF2","Gruve.F4") 
group2b <- c("Gruve.F5","Gruve.F7") 
# Filter using grepl() on Shortname:
group3 <- "OTR"     # left side
# Filter using the two first characters (using substr() on Shortname):
group4a1 <- c("24", "25", "26")        # right straight  
group4a2 <- c("29")        # right down  
group4b <- c("27", "28", "24")   # left
group4c <- c("20", "21")    # left
group5 <- c("10", "11", "12")    # left
group6 <- c("04", "05", "06")               # right
group7 <- c("01","02","03")    # left

# For setting ylim:
ggdata <- layer_data(gg_back)

gg2 <- gg_back +
  geom_path(data = df_rivers_strahler7,
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes_mjosa,
               aes(group = group), col = rivercol, fill = rivercol) +
  # only in quality map, not label map:
  theme(legend.position = "none") +        
  # only in label map, not in quality map:
  # geom_point(
  #   data = df_stations,
  #   aes(label = Shortname, shape = Stasjonstype, fill = Stasjonstype), size = rel(2)) +
  # scale_fill_brewer(palette = "Set1") +
  # scale_shape_manual(values = c(21,22,24)) +
  
  # The next three label groups are mines (Gruve) - shall not be included here:
  #
  # geom_text_right(
  #   aes(label = Shortname), 
  #   data = df_stations %>% filter(Shortname %in% group1), 
  #   xdist = 30E3, y_even_dist = 20E3, xadj_start = 7E3,
  #   color = "blue3", segment.color = "blue3") +
  # geom_text_left(
  #   aes(label = Shortname), 
  #   data = df_stations %>% filter(Shortname %in% group2a), 
  #   xdist = 20E3, y_even_dist = 20E3, y_even_pos = 40E3, xadj_start = 7E3,
  #   order = "E to W",
  #   color = "blue3", segment.color = "blue3") +
  # geom_text_right(
  #   aes(label = Shortname), 
  #   data = df_stations %>% filter(Shortname %in% group2b), 
  #   xdist = 20E3, y_even_dist = 20E3, y_even_pos = -35E3, xadj_start = 7E3,
  #   color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(grepl("OTR", Shortname)), 
    xdist = 30E3, xadj_start = 7E3, 
    y_even_dist = 20E3, order = "N to S",
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group4a1), 
    xdist = 30E3, xadj_start = 7E3, 
    y_even_dist = 20E3, order = "N to S",
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group4a2), 
    xdist = 30E3, xadj_start = 7E3, 
    y_even_dist = 20E3, order = "N to S", y_even_pos = -30E3,
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group4b), 
    xdist = 40E3, xadj_start = 7E3, y_even_dist = 20E3, y_even_pos = 50E3, 
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group4c), 
    xdist = 30E3, xadj_start = 7E3,
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group5), 
    xdist = 40E3, xadj_start = 7E3, y_even_dist = 20E3, y_even_pos = 20E3, 
    color = "blue3", segment.color = "blue3") +
  geom_text_right(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group6), 
    xdist = 30E3, xadj_start = 7E3, y_even_dist = 20E3, 
    order = "N to S",
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = df_stations %>% filter(substr(Shortname,1,2) %in% group7), 
    xdist = 40E3, xadj_start = 7E3, y_even_dist = 20E3, y_even_pos = -5E3, 
    color = "blue3", segment.color = "blue3") +
  # only in quality map, not label map:
  geom_subview(data = df_pies %>% filter(!Shortname %in% c(group1, group2a, group2b)), 
               aes(x = x, y = y, subview = pie, width = width, height = height)) +
  xlim(range(ggdata$x) + c(-50E3, 50E3)) +  
  ylim(range(ggdata$y) + c(-50E3, 0))   

# gg2

if (save_plots){
  fn <- glue("{folder_fig}/07c_qualitymap_outside_boxes2.png")
  scale <- 1.5
  ggsave(fn, gg2, width = 18*scale, height = 25*scale, units = "cm", dpi = 500/scale)  
}

```


### c. Map with inset boxes    
```{r, fig.width=8, fig.height=10}

#
# Make data set for the letters beside the box
#
box_letter_pos <- box_polygons %>%
  group_by(boxnumber) %>%
  summarise(
    x = max(x) + 7E3,  # left of left edge 
    y = max(y))         # top edge (we use vjust to adjust the position)
box_letter_pos$letter <- LETTERS[as.numeric(box_letter_pos$boxnumber)]
box_letter_pos

#
# Add boxes and letters
#
gg3 <- gg2 +
  geom_polygon(data = box_polygons, aes(group = boxnumber),
               fill = NA, colour = "red3", size = rel(1.5)) +
  geom_text(data = box_letter_pos, aes(label = letter), 
            size = rel(8), colour = "red3", hjust = 0, vjust = 1) 

# gg3

```

## 5. Insets  
These plots differ form the 
```{r}

gg_box <- vector("list", length(box_polygons))
data_box <- vector("list", length(box_polygons))

```

### Defining functions  
```{r}

#
# Function for making 'data_box', which is the data for the pies
#   inside box number 'i'
#
# sizeratio = 0.15 is found by trial and error
#

qualplot_make_data_box <- function(i, polygon, data, sizeratio = 0.15){
  
  data_box[[i]]  <- data %>%
    filter(
      (x > min(polygon$x) & x < max(polygon$x) & 
         y > min(polygon$y) & y < max(polygon$y))
    )
  
  data_box[[i]] %>%
    mutate(width = width*sizeratio,
           height = height*sizeratio)
}


#
# Function for adding pies for box number 'i'
# (which we do *after* adding labels)
#
qualplot_add_pies <- function(gg, data, box, i) {
  
  gg <- gg +
    geom_subview(data = data, 
                 aes(x = x, y = y, subview = pie, width = width, height = height)) +
    annotate("text", label = LETTERS[i], 
             x = min(box$x) + 1200, y = max(box$y) - 1500, 
             size = rel(8), colour = "red3") +
    coord_fixed(xlim = range(box$x), ylim = range(box$y)) +
      theme(legend.position = "none",
            plot.background = element_rect(
              colour = "black",
              size = 1)
            )

}

                                 

```

### Inset 1
```{r, fig.width = 5, fig.height = 5}

# ------------------ ************************ ------------------- #
#
# HOW TO CODE
# For each inset 1-5:
#   - the TOP (except "i <- 1") and BOTTOM parts are always the same
#   - the MIDDLE part between A and B (adding labels) is copy-pasted 
#   from script 07b (yes, I know...)
#
# ------------------ ************************ ------------------- #

i <- 1

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back +
  geom_path(data = df_rivers_strahler5, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol)
  
# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("43","46") ~ "left",
    substr(Shortname,1,2) %in% "45" ~ "above",
    TRUE ~ "right"))

# Add levels
gg_box[[i]] <- gg_box[[i]] +
  # The rest is copied from the corresponding place in 07b...2021
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]],
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3")

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```

### Inset 2
```{r, fig.width = 5, fig.height = 5}

# ------------------ ************************ ------------------- #
# HOW TO CODE: see comment for inset 1
# ------------------ ************************ ------------------- #

i <- 2

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back +
  geom_path(data = df_rivers_strahler5, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol)
  
# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("33","36") ~ "above",
    TRUE ~ "below"))

# Add labels  
gg_box[[i]] <- gg_box[[i]] %>%
  add_label_above(data = data_box[[i]] %>% filter(group == "above"),
                  color = "blue3", segment.color = "blue3", hjust = c(0,1)) %>%
  add_label_below(data = data_box[[i]] %>% filter(group == "below"),
                  color = "blue3", segment.color = "blue3", hjust = 0)


# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```
### Inset 3
```{r, fig.width = 5, fig.height = 5}

# ------------------ ************************ ------------------- #
# HOW TO CODE: see comment for inset 1
# ------------------ ************************ ------------------- #

i <- 3

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back +
  geom_path(data = df_rivers_strahler5, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol)
  
# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
data_box[[i]] <- data_box[[i]] %>%
  mutate(group = case_when(
    substr(Shortname,1,2) %in% c("13") ~ "right",
    TRUE ~ "left"))

# Add labels  
gg_box[[i]] <- gg_box[[i]] +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "right"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3") +
  geom_text_left(
    aes(label = Shortname), 
    data = data_box[[i]] %>% filter(group == "left"),
    xdist = 3.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3")


# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```

### Inset 4
```{r, fig.width = 5, fig.height = 5}

# ------------------ ************************ ------------------- #
# HOW TO CODE: see comment for inset 1
# ------------------ ************************ ------------------- #

i <- 4

box <- box_polygons %>% filter(boxnumber == i)
data_box[[i]] <- qualplot_make_data_box(i, box, df_pies)
gg_box[[i]] <- gg_back +
  geom_path(data = df_rivers_strahler5, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol)
  
# ------------------ A ------------------- #

# Add 'group' (we will make different labels for each group)
# Not needed in this case

# Add labels  
# gg_box[[i]] <- gg_box[[i]] +
gg_box[[i]]  <- gg_box[[i]] +
  geom_text_right(
    aes(label = Shortname), 
    data = data_box[[i]],
    xdist = 2.5E3, same_x = FALSE, xadj_start = 900, 
    color = "blue3", segment.color = "blue3")

# ------------------ B ------------------- #
  
gg_box[[i]] <- qualplot_add_pies(gg_box[[i]], data_box[[i]], box, i)


# gg_box[[i]]

```


## 6. Final map
```{r}

# Positions on scale 0 to 1 (of lower left corner)
# Copied from 07b 2021 version
box_pos <- tibble::tribble(
  ~x,    ~y,
  0.78,  0.15,
  0.19,  0.551,
  0.19,  0.291,  # 
  0.19,  0.15
)

# Size, given on scale 0 to 1 
# box_dim$x[2] = 0.3 in size:
box_dim$x_scale = box_dim$x/box_dim$x[2]*0.3
box_dim$y_scale = box_dim$y/box_dim$x[2]*0.3

# Start plot (everything except the insets)
gg4 <- ggdraw() +
  draw_plot(gg3, x = 0.15, y = 0, scale = 0.7)

# Add
for (i in seq_along(gg_box)){
  gg4 <- gg4 + draw_plot(
    gg_box[[i]], 
    x = box_pos$x[i], y = box_pos$y[i], 
    width = box_dim$x_scale[i], height = box_dim$y_scale[i]
    )
  }

if (save_plots){
  fn1 <- glue("{folder_fig}/07c_qualitymap_complete.png")
  fn2 <- glue("{folder_fig}/07c_qualitymap_complete_hi.png")
  # fn <- glue("{folder_fig}/07c_qualitymap_TEST.png")
  scale <- 1.5
  ggsave(fn1, gg4, width = 18*scale, height = 25*scale, units = "cm", dpi = 500/scale)  
  ggsave(fn2, gg4, width = 18*scale, height = 25*scale, units = "cm", dpi = 1000/scale)  
}

```


