---
title: "Untitled"
author: "DHJ"
date: "May 2022"
output: html_document
---


"Quality maps" showing one pie per station for Results chapter     
* Pie: color of left half shows ecological quality, colour of right half chemical quality  
  
## Code overview   
* 2a: loads data (in 2021, also inset map coordinates)    
* 2b-d: County map data is built up from scratch, as in script 7b   
* 3.  
    - Makes pie ggplot objects using the functions make_pie() and make_pie_from_colours()   
    - These are stored in the column 'pie' in th data frame 'df_pies'   
* 4. Make main map (all symbols, but labels are outside inset boxes only)   
    - Very similar to script 7b   
    - However, since 7b stores ggplot objects, not position of labels, much code is copy-pasted
    from script 7b   
* 5. Make inset plots   
    - None this year     

## 1. Prerequisites  

### a. Whether and where to save figures  
```{r}
#
# Save figures to file, or just show them in this report?
#

# save_plots <- TRUE
save_plots <- FALSE


#
# Where to save figures
#
folder_fig <- "Figures/2022_main"


```

### b. Libs + map  
```{r}

library(tidyverse)  # filter, group_by, summary, etc.
library(gridGraphics)
library(maps)       # Norway map (NOTE: must be loaded after tidyverse)
library(readxl)

# map_norway <- map_data("world", "Norway")
# map_norway_h <- readRDS("Data_input/map_norway_hires.RData")

# Long/lat map (including the smaller islands) - lacking Mjøsa, though! 
#   (and including some North Finnish lakes?)
load("Data_input/Norway_coastline_longlat2.RData")
# rename
map_norway_h <- norway_coast_longlat2
rm(norway_coast_longlat)

# Test plot
# ggplot(map_norway_h) + geom_path(aes(long, lat, group = group))

library(mapproj)    # mapproject
library(ggrepel)    # geom_text_repel()
library(sp)         # SpatialPoints(), CRS(), spTransform()
library(sf)         # st_read
library(ggimage)    # geom_subview(), theme_transparent()

library(glue)       # used in ggplot2() function
library(leaflet)

library(cowplot)

source("07_Figures_functions.R")

# Define crs strings for conversion between long/lat and UTM
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"

```
### c. Define colours for classes  
```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no



```

## 2. Data   

### a1. Data from script 7a and 7b  
```{r}

# From script 7a
df_index <- readRDS("Data/2022/07a_df_index_2021.rds")
df_index_barplot <- readRDS("Data/2022/07a_df_index_barplot_2021.rds")


# From script 7b, part 4c
# From script 7b, part 2.a2
df_stations_all <- read.csv("Data_input/2022/KartOgFigurgrunnlag2021.csv",
                            encoding = "UTF-8")  

# Not relevant:
# box_dim <- readRDS("Data/2022/07b_box_dim.rds")
# box_polygons <- readRDS("Data/2022/07b_box_polygons.rds")

```


### a2. Plot all stations  

```{r}

ggplot(df_stations_all, aes(Long, Lat)) +
  geom_point() +
  coord_map("lambert", 15, 65)  

```

### a3. Split into North and South Norway    

* Not relevant here  


### b1. Map with counties (fylke)   

* 
```{r}
# 
# Gotten from Geonorge ("Norske fylker og kommuner illustrasjonsdata 2019 (klippet etter kyst)")
#   https://kartkatalog.geonorge.no/metadata/cb02ab77-d3e6-4500-8a92-ea67367e7734 
#   https://nedlasting.geonorge.no/geonorge/Generell/AdmEnh_klippet_etter_kyst2019.zip  
map_counties_utm33 <- sf::st_read("Data_input/2021_map/fylker2021.json")
# UTM zone 33
# plot(map_counties_utm)

```

### b2. Make simplified coastline  
* Using 'st_simplify'  
    - reduces size from 17 MB to 0.6 MB  
    - see https://www.r-bloggers.com/2021/03/simplifying-geospatial-features-in-r-with-sf-and-rmapshaper/   
    - The simplification changes the geometry column from MULTIPOLYGON to GEOMETRY,
    we must change it back (otherwise `st_coordinates`doesn't work)  
    - See https://cran.r-project.org/web/packages/sf/vignettes/sf3.html  

```{r}

map_counties_utm33_simple <- st_simplify(map_counties_utm33,
                                         preserveTopology = FALSE, dTolerance = 500)

# The simplification () changes the geometry column from to GEOMEtry
# Check:
# class(map_counties_utm33$geometry)         # "sfc_MULTIPOLYGON" "sfc"
# class(map_counties_utm33_simple$geometry)  # "sfc_GEOMETRY" "sfc"
# We change it back like this: 
#  (ref: https://cran.r-project.org/web/packages/sf/vignettes/sf3.html)

map_counties_utm33_simple$geometry <- st_cast(
  map_counties_utm33_simple$geometry, "MULTIPOLYGON")

```

### c. Get coordinates of county map (df_counties_all)  
Used to make the background map  
* We convert the map from UTM zone 33 to UTM 32, as this is more fitting for Southern Norway   (https://upload.wikimedia.org/wikipedia/commons/9/9e/LA2-Europe-UTM-zones.png)
```{r}

map_to_dataframe <- function(map_object){
  st_coordinates(map_object) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2, id = L3)
}

# Extract coordinates and Transform from UTM33 to UTM32
df_counties_all <- map_to_dataframe(map_counties_utm33)
df_counties_all_simple <- map_to_dataframe(map_counties_utm33_simple)

nrow(df_counties_all)
nrow(df_counties_all_simple)
# [1] 798273
# [1] 20095
```



### d. Make background map (gg1_back)    
```{r}

# Check counties: it turns out that 5 = Nordland, 10 = Troms + Finnmark

if (FALSE){
  df_counties_all %>% 
    filter(L1 == 1) %>%
    group_by(id) %>%
    summarise(across(, mean)) %>%
    arrange(y) %>%
    ggplot(aes(x, y, label = id)) +
    geom_text() +
    coord_equal(ratio = 0.5) 
}

# Keep these 4 counties (Trøndelag + Nordland)
# - for both full and simple version
df_counties_full <- df_counties_all %>%
  filter(id %in% c(9,5,6,11))
df_counties_simp <- df_counties_all_simple %>%
  filter(id %in% c(9,5,6,11))

# Get remaining county numbers
county_numbers <- unique(df_counties_simp$id)

# Make gg 

gg_from_counties_coastline <- function(mapdata){
  
  result <- ggplot(data = mapdata, aes(x, y)) + 
    geom_blank() + 
    coord_fixed() +
    theme_minimal() +
    theme(panel.grid = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
    )
  
  # Add one county after the other
  for (i in county_numbers){
    result <- result + 
      geom_polygon(data = mapdata %>% filter(L1 == 1 & id %in% i), 
                   aes(x, y, group = group), fill = "navajowhite", color = "grey30")
  }
  
  invisible(result)
  
}

# Start 'gg_back_full'
gg_back_full <- gg_from_counties_coastline(df_counties_full)
gg_back_simp <- gg_from_counties_coastline(df_counties_simp)

# test use of ggdata
if (FALSE)
  gg_back_simp + ylim(range(ggdata$y) + c(-100E3, 0))

```

### e1. Rivers

```{r}

nc_rivers_strahler4_full <- st_read(
  "K:\\Kart\\ELVIS\\Hovedelv\\elvis_hovedelv.shp",
  query = "SELECT * FROM elvis_hovedelv WHERE STRAHLER >= 4")  # only big rivers; saves a little time
#  UTM zone 33

# Turns out to be harder to simplify rivers (they fall apart...)
simplify_rivers <- FALSE  
# simplify_rivers <- TRUE  

if (simplify_rivers){
  
  nc_rivers_strahler4 <- st_simplify(nc_rivers_strahler4_full,
                                     preserveTopology = FALSE, dTolerance = 100)
  # Check class of geometry:
  # nc_rivers_strahler4_full[["_ogr_geometry_"]][1] %>% class()
  nc_rivers_strahler4[["_ogr_geometry_"]] <- st_cast(
    nc_rivers_strahler4[["_ogr_geometry_"]], "MULTILINESTRING")
  
} else {
  
  nc_rivers_strahler4 <- nc_rivers_strahler4_full
  
}

# Extract coordinates and Transform from UTM33 to UTM32
df_rivers_strahler5 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 5) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000)  # Fix errors (i.e. remove extremely long segments)

df_rivers_strahler6 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 6) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000) # Fix errors (i.e. remove extremely long segments)

df_rivers_strahler7 <- nc_rivers_strahler4 %>%
  filter(STRAHLER >= 7) %>% 
  st_coordinates %>%
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2) %>%
  fix_river_errors(limit_meters = 2000) # Fix errors (i.e. remove extremely long segments)

range(df_counties_full$y)
south_limit <- min(df_counties_full$y) - 300000 # 300 km S and N of limits
north_limit <- max(df_counties_full$y) + 300000

# Remove data for North Norway (filter doesn't work, as some data are reshuffeled)
# sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y < south_limit  
# df_rivers_strahler5[sel, c("x","y")] <- NA
# sel <- !is.na(df_rivers_strahler5$y) & df_rivers_strahler5$y > north_limit  
# df_rivers_strahler5[sel, c("x","y")] <- NA
# 
# sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y < south_limit
# df_rivers_strahler7[sel, c("x","y")] <- NA
# sel <- !is.na(df_rivers_strahler7$y) & df_rivers_strahler7$y > north_limit
# df_rivers_strahler7[sel, c("x","y")] <- NA

rivercol <- "lightskyblue"

```

### e2 Plot rivers  
```{r}

if (TRUE){
  
  # Test plot
  gg_back_simp +
    geom_path(data = df_rivers_strahler6, aes(x, y, group = group), col = "red") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))
}
  
if (FALSE){

  gg_back_simp +
    geom_path(data = df_rivers_strahler6_full, aes(x, y, group = group), col = "red") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))

}

```

### f1. Lakes  

Get coordinates (in zone 32)   
```{r}

nc_lakes_full <- st_read("K:/Kart/N1000/VANN.shp")
st_crs(nc_lakes_full) <- "+proj=utm +zone=33"  # set coordinate system

# Turns out to be harder to simplify rivers (they fall apart...)
simplify_lakes <- FALSE  
# simplify_lakes <- TRUE  

if (simplify_lakes){
  
  nc_lakes <- st_simplify(nc_lakes_full,
                                     preserveTopology = FALSE, dTolerance = 300)
  # Check class of geometry:
  # nc_lakes[["_ogr_geometry_"]][1] %>% class()
  nc_lakes[["geometry"]] <- st_cast(
    nc_lakes[["geometry"]], "POLYGON")
  
} else {
  
  nc_lakes <- nc_lakes_full
  
}

# Extract coordinates and Transform from UTM33 to UTM32
df_lakes <- st_coordinates(nc_lakes) %>% 
  as.data.frame() %>%
  add_transformed_coord(
    name_x = "X", name_y = "Y", 
    from = "utm", from_zone = 33,
    to = "utm", to_zone = 32
  ) %>%
  select(-X, -Y) %>%
  rename(group = L2)

# Mjøsa only 
df_lakes_mjosa <- df_lakes %>% filter(group == 3462)

```


### f2. Plot lakes    
```{r}

if (TRUE){
  
  # Test plot (just part of the area)  
  gg_back_simp +
    geom_polygon(data = df_lakes, aes(x, y, group = group), col = "red", fill = "blue3") +
    coord_fixed(xlim = c(7E5 + c(-1E5,1E5)), 
                ylim = c(72E5 + c(-1E5,1E5)))
}
  
```


## 3. Make pies  

### a. Start making 'df_pies'  
Also writes df_stations_vf to excel (later manipulated semi-manually and used in part 6)    
- Note that we use 'df_stations_all', i.e. also include the Northern ones   
```{r}

# Start with location data on Vannforekomst-level
df_pies_all <- df_stations_all %>%
  left_join(df_index_barplot %>% select(Rapportnavn, nEQR_ecol_klasse),
            by = c("Shortname" = "Rapportnavn")) %>%
  rename(Class_ecol = nEQR_ecol_klasse)


```


### b. Ecological class, levels and colors    
```{r}


# df_colors$Status_no
# class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")


df_pies_all <- df_pies_all %>%
  left_join(
    df_colors %>% select(Status_no, Class_color),
    by = c("Class_ecol" = "Status_no")
  ) %>%
  rename(Colour_ecol = Class_color)  

ggplot(df_pies_all, aes(Class_ecol, Index_ecol, fill = Class_ecol)) + 
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = class_colors, drop = FALSE) +
  theme(panel.background = element_rect(fill = "grey70"), panel.grid = element_blank())

```


### c. Chemical class, levels and colors    

```{r}

df_pies_all <- df_pies_all %>%
  mutate(
    Colour_chem = case_when(
      is.na(Class_chem) ~ class_colors["Uklassifisert"],
      Class_chem %in% "God" ~ class_colors["Svært god"],
      Class_chem %in% "Ikke god" ~ class_colors["Svært dårlig"],
      Class_chem %in% c("i.d.", "ID") ~ class_colors["Uklassifisert"])
  )

xtabs(~addNA(Colour_chem) + addNA(Class_chem), df_pies_all)

```


### d. Make pies from data frame 'df_pies_all', and add to 'df_pies_all'  

```{r, fig.width=3, fig.height=3}      

# Function - make pie for line number i
make_pie_linenumber_indexvalues <- function(i){
  df <- df_pies_all[i, c("Colour_ecol", "Colour_chem")]
  make_pie_from_colours(as.character(df))
}

# TEST
make_pie_linenumber_indexvalues(1)
make_pie_linenumber_indexvalues(2)
make_pie_linenumber_indexvalues(3)

# test - should make 3 plots with one pie in each  
if (FALSE){
  grep("03.ORK1", df_pies_all$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("02.ORK2", df_pies_all$Shortname) %>% make_pie_linenumber_indexvalues()
  grep("01.ORK3", df_pies_all$Shortname) %>% make_pie_linenumber_indexvalues()
}

# Make all pies (a list)
pies <- 1:nrow(df_pies_all) %>% purrr::map(~make_pie_linenumber_indexvalues(.))
length(pies)
# check:
# pies[[1]]

# Add pies to dataframe (as a list column)
df_pies_all$pie = pies
# check:
# df_pies_all$pie[1]

# df <- df_pies_all %>% filter(!Shortname %in% c(group1, group2a, group2b))
# df$pie[1]

```

### e. Test  
```{r}

df_pies_test <- df_pies_all[c(1,5,10),]

#
# Width and height of pies
#   
df_pies_test$width = 250E3    # Sets size of pies
df_pies_test$height = 250E3   

gg <- gg_back_simp +
  geom_point(data = df_pies_test, aes(x = x, y = y))
gg

```

## 4. Map outside boxes  

* We didn't have to make any boxes this time, so this is the entire map     

### a. Test plot    
```{r}

# Pick all pies    
df_pies <- df_pies_all

# For the ones in Southern Norway: use
#   filter(Lat < 65)

#
# Width and height of pies
#   
df_pies$width = 14E3    # Sets size of pies
df_pies$height = 14E3   

#
# Make data set for stations outside inset plots
#

df_pies_outside <- df_pies

#
# All pies are outside so we skip the next part  
#
# for (i in unique(box_polygons$boxnumber)){
#   box <- box_polygons %>% filter(boxnumber == i)
#   df_pies_outside <- df_pies_outside %>%
#     filter(
#       !(x > min(box$x) & x < max(box$x) & y > min(box$y) & y < max(box$y))
#     )
# }

gg1 <- gg_back_simp +
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               )
# gg

if (save_plots){  
  fn <- glue("{folder_fig}/07c_quality_no_rivers_lakes.png")
  scale <- 1.5
  ggsave(fn, gg1, width = 18*scale, height = 25*scale, 
         units = "cm", dpi = 500/scale)  
}

```


### b. Make a ggplot without labels and save as svg   

* Makes quality (cake) figure named 'without_labels' in svg format   
    - Also include points 
* Copied labels from label map and adjusted them  
    - Opened in Inkscape and saved as `07c_quality_strahler6_with_labels_adjusted.svg`  
    - Also opened label map `07b_labelmap_strahler6_with_labels_adjusted.svg` in Inkscape  
    - Select labels using Edit : Select same : Object type  
    - Copy  
    - Paste using Edit : Paste in place   
* Edited label and pie placements in Inkscape   
    - When we had to move a pie, we added a line (width 1.5) between the point and the pie (see final figure)   
* Add legend  
    - Colors and text, see below (part c)  
    - the small circle copied from`Qualitymap_2021_legend.svg`   
* Set background to white and export to `.png` (see tips in script 07b part 4)   

    
```{r, fig.width=8, fig.height=10}

gg1 <- gg_back_simp +
  geom_path(data = df_rivers_strahler6, 
            aes(group = group), col = rivercol) +
  geom_polygon(data = df_lakes, 
               aes(group = group), col = rivercol, fill = rivercol) +
  # Add points - normally covered by the pies, but are used if we have to move overlapping pies in Inkscape
  # - see final file '07c_quality_strahler6_with_labels_adjusted'  
  geom_point(data = df_pies_outside, 
             shape = 15, size = rel(1)) +
  # Add pies  
  geom_subview(data = df_pies_outside, 
               aes(x = x, y = y, subview = pie, width = width, height = height)
               ) +
  # Extent exactly the same as for 7b map ("labelmap")  
  # - this facilitates copy-paste of labels  
  coord_fixed(xlim = c(400000, 800000), ylim = c(6.95E6, 7.5E6))


# ggsave2("{folder_fig}/07b_labelmap_without_labels.svg", gg1, width = 8, height = 12)
# Not used

ggsave2("{folder_fig}/07c_quality_strahler6_without_labels.svg", 
        gg1, width = 8, height = 12)

```


### c. Plot for legend   

* For the fill color and text part of the legend (copy-pasted to the map)

```{r}

levels(df_colors$Status_no) %>% rev() %>% dput()

order_for_legend <- c("Svært god", "God", "Moderat", "Dårlig", "Svært dårlig", "Uklassifisert")

df_colors_for_legend <- df_colors %>%
  mutate(Status_no = factor(Status_no, levels = order_for_legend)) %>%
  arrange(Status_no)

cols <- df_colors_for_legend$Class_color
names(cols) <- df_colors_for_legend$Status_no
  
gg_figure_for_legend <- ggplot(df_colors_for_legend, aes(x = Status_no,  fill = Status_no)) +
  scale_fill_manual(values = cols) +
  geom_bar() +
  theme(legend.text = element_text(size = 15),
        legend.key.size = unit(0.8, "cm"))

ggsave2("{folder_fig}/07b_quality_figure_for_legend.svg", 
        gg_figure_for_legend, width = 8, height = 5)

# ggsave2("{folder_fig}/07b_quality_figure_for_legend.svg", 
#         gg_figure_for_legend, width = 14, height = 9)

```




