---
title: "20_4stations_2021"
author: "DHJ"
date: "10 3 2021"
output: 
  html_document:
    keep_md: true  
    toc: true  
    toc_float: true
---

## 1. Libs  
```{r}

# install.packages("OpenStreetMap")
suppressPackageStartupMessages (library(dplyr))
suppressPackageStartupMessages (library(OpenStreetMap))
suppressPackageStartupMessages (library(maps))
suppressPackageStartupMessages (library(ggplot2))
suppressPackageStartupMessages (library(readxl))
suppressPackageStartupMessages (library(sf))

suppressPackageStartupMessages(library(plotrix))  # for polygon.shadow() (and more?) 
                  #   used in floating.pie()

# Not strictly necessary:
suppressPackageStartupMessages(library(mapview))

# CRS strongs for changing projection
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"
crs_utm33 <- "+proj=utm +zone=33 +ellps=WGS84 +datum=WGS84 +units=m"


```
### Define colours for classes  
```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_kort = case_when(
      Status %in% "High" ~ "SG",
      Status %in% "Good" ~ "G",
      Status %in% "Moderate" ~ "M",
      Status %in% "Poor" ~ "D",
      Status %in% "Bad" ~ "SD",
      Status %in% "Unclassified" ~ "NA"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no

```

## 2. Data  
```{r}

fn <- "C:/Data/seksjon 318/Elveovervakning/Data_input/2021/Klassifisering av økologisk tilstand i elver for rapport 2020.xlsx"
# readxl::excel_sheets(fn)

dat <- read_excel(fn, sheet = "Til Dag ") %>%
  mutate(Lat = as.numeric(Lat),
         Long = as.numeric(Long))

n1 <- nrow(dat)

```

### Add colors   
One color column for each of the columns Påvekstalger, HBI, Bunndyr
```{r}

dat <- dat %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Påvekst_col = Class_color),
            by = c("Påvekstalger" = "Status_kort")) %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(HBI_col = Class_color),
            by = c("HBI" = "Status_kort")) %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Bunndyr_col = Class_color),
            by = c("Bunndyr" = "Status_kort"))

n2 <- nrow(dat)

if (n1 != n2)
  stop("Error! number of lines changed!")

```


### Change to spatial data (long-lat and UTM projections)    
* Need to change to sf (or sp) object in order to transform data   
* Also, sf data are easy to plot in mapvies (next chunk)  
```{r}

# For easxy plotting in mapvio 
# For easxy plotting in mapvio 
datsf_longlat <- sf::st_as_sf(
  dat,
  coords = c("Long", "Lat"), 
  crs = crs_longlat, 
  agr = "constant")  

# Transform to UTM
datsf <- st_transform(datsf_longlat, crs_utm)  

# Transform to Web mercator
datsf_wm <- st_transform(datsf_longlat, 3857)  

```

### Interactive map  
```{r}

mapview(datsf_longlat, zcol = "Elv")

```

## 3a. Test for one area, plot in UTM   
### OpenStreetMap data   
* The data from OpenStreetmap are in web mercator projection  
```{r, results='hide', warning=FALSE, message=FALSE}

river <- "Moelva"

df <- dat %>%
  filter(Elv == river)

# Size of area, measured in dregrees long/lat  
dlat <- 0.05
dlon <- 0.10

# p1 = upper 
p1 <- c(mean(range(df$Lat)) + dlat/2, mean(range(df$Long)) - dlon/2)
p2 <- c(mean(range(df$Lat)) - dlat/2, mean(range(df$Long)) + dlon/2)

mp_webmerc <- openmap(p1, p2, type = 'osm')  
plot(mp_webmerc)

# Test function:
# x <- get_map("Moelva", data = dat, dlon = 0.10, dlat = 0.05)
# plot(x)

```

### Other map types  
```{r}



```

### Check all plot types    
```{r, warning = FALSE}

maptypes <- c("osm", "osm-bw",
              "maptoolkit-topo", "waze", "bing", "stamen-toner", "stamen-terrain",
              "stamen-watercolor", "osm-german", "osm-wanderreitkarte", "mapbox", "esri",
              "esri-topo", "nps", "apple-iphoto", "skobbler", "hillshade", "opencyclemap",
              "osm-transport", "osm-public-transport", "osm-bbike", "osm-bbike-german")

for (maptype in maptypes){
  # maptype <- 'osm'
  test <- try(openmap(p1, p2, type = maptype))
  if (class(test) != "try-error"){
    plot(test)
    mtext(maptype)
  }
}

```


### Change to UTM and plot    
* Note that the map is a bit 'tilted' due to the difference between UTM and Web mercator 
```{r}

mp <- openproj(mp_webmerc, projection = crs_utm)
plot(mp)  

```
### Add pie using plotrix::floating.pie  

* Original version of 'floating.pie' gave a kind of flattened pie   
* Made new version of 'floating.pie' where aspect can be set by user   
* Didnt find a good way to set aspect, we use aspect1 + "trial & error" factor (0.8)  
```{r}


river_data <- datsf %>%
  filter(Elv == river)

coord <- river_data %>% 
  st_coordinates() %>%
  as.data.frame()

river_data <- bind_cols(river_data, coord)

# Aspect from plot dimsnsions (used in the original version of floating.pie)
aspect1 <- par("pin")[1]/par("pin")[2]
# Aspect from bounding box of map 
aspect2 <- (mp$bbox$p2[1] - mp$bbox$p1[1]) / (mp$bbox$p1[2] - mp$bbox$p2[2])

# Plot map, plus points as test
plot(mp)  
points(river_data$X, river_data$Y, pch = 18, col = "red", cex = 2)

# Plot pies (with just random data)
# args(floating.pie)
i <- 1   # the Southern one
floating.pie(river_data$X[i], river_data$Y[i], c(2,4,4,2,8), radius=200,
             col=c("#ff0000","#80ff00","#00ffff","#44bbff","#8000ff"))
i <- 2
floating.pie(river_data$X[i], river_data$Y[i], c(2,4,4,2,8), radius=200,
             col=c("#ff0000","#80ff00","#00ffff","#44bbff","#8000ff"), aspect = aspect2)
i <- 3   # the Northern one
floating.pie(river_data$X[i], river_data$Y[i], c(2,4,4,2,8), radius=200,
             col=c("#ff0000","#80ff00","#00ffff","#44bbff","#8000ff"), aspect = aspect1*0.8)  # set by trial and error  

# ?plot.OpenStreetMap


```
### Plot actual pies     
```{r}

plot(mp)  

# Plot pies (with just random data)
# args(floating.pie)
for (i in 1:3)
  floating.pie(river_data$X[i], river_data$Y[i], c(1,1,1), radius=200,
               col=c(river_data$Påvekst_col[i], 
                     river_data$HBI_col[i], 
                     river_data$Bunndyr_col[i]), 
               aspect = aspect1*0.8)  # set by trial

```

## 3b. Test for one area, plot in Web mercator coordinates  


```{r}

plot(mp_webmerc)




```

### Add pie using plotrix::floating.pie    
* Again, we get a flattened pie if we don't adjust aspect  
* But the map isn't tilted, at least  
* Choose this way  
```{r}

# As in 3a, but use datsf_wm instead of datsf
river_data <- datsf_wm %>%
  filter(Elv == river)

coord <- river_data %>% 
  st_coordinates() %>%
  as.data.frame()

river_data <- bind_cols(river_data, coord)

# Plot map, plus points as test
# As in 3a, but use mp_webmerc
plot(mp_webmerc)  
points(river_data$X, river_data$Y, pch = 18, col = "red", cex = 2)

# Aspect from plot dimsnsions (used in the original version of floating.pie)
aspect1 <- par("pin")[1]/par("pin")[2]
# Aspect from bounding box of map 
aspect2 <- (mp$bbox$p2[1] - mp$bbox$p1[1]) / (mp$bbox$p1[2] - mp$bbox$p2[2])

# Plot pies (with just random data)
# args(floating.pie)
i <- 1   # the Southern one
floating.pie(river_data$X[i], river_data$Y[i], c(2,4,4,2,8), radius=400,
             col=c("#ff0000","#80ff00","#00ffff","#44bbff","#8000ff"))
i <- 2
floating.pie(river_data$X[i], river_data$Y[i], c(2,4,4,2,8), radius=400,
             col=c("#ff0000","#80ff00","#00ffff","#44bbff","#8000ff"), aspect = aspect2)
i <- 3   # the Northern one
floating.pie(river_data$X[i], river_data$Y[i], c(2,4,4,2,8), radius=400,
             col=c("#ff0000","#80ff00","#00ffff","#44bbff","#8000ff"), aspect = aspect1*0.8)
# set by trial and error  

# ?plot.OpenStreetMap


```

```{r}

plot(mp_webmerc)  
vannfor_ids <- unique(river_data$`Vannforekomst ID`)
j <- 3
vannfor_list <- get_riverdata(vannfor_ids[j])
# debugonce(get_riverlines_wm)
river_coord_all <- get_riverlines_wm(vannfor_list)
river_coord_list <- river_coord_all %>% split(.$ID)
for (river_coord in river_coord_list)
  lines(river_coord[,"X"], river_coord[,"Y"], col = "red", lwd = 5)

# View(river_coord_list[[1]])

```



## 4. Plot river + text for each Vannforekomst    

### Test for maing function 
```{r}

plot(mp_webmerc)  
vannfor_ids <- unique(river_data$`Vannforekomst ID`)
river_coord <- river_coord_list[[1]]

for (j in seq_along(vannfor_ids)){
  
  # j <- 2
  
  vannfor_list <- get_riverdata(vannfor_ids[j])
  # debugonce(get_riverlines_wm)
  river_coord_all <- get_riverlines_wm(vannfor_list)
  
  # Split 'river_coord_all' into a list of data frames (one per segment)
  river_coord_list <- river_coord_all %>% split(.$ID)
  
  # Plot river, segment by segment
  for (river_coord in river_coord_list)
    lines(river_coord[,"X"], river_coord[,"Y"], col = "blue", lwd = 4)
  
  # Get positions for text
  text_coord <- get_textpos_webmerc(river_coord_all, "right", 300)
  
  # PLot text - here: right of river
  text(text_coord$X, text_coord$Y, vannfor_ids[j], adj = text_coord$adj)
  
}


```


### Test of function
```{r}

plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "right"),
            id_distance = 250, 
            data = dat)

plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = -500, 
            data = dat)

plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
            id_pos = c("below", "below"),
            id_distance = c(0, 200), 
            data = dat)

plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
            id_pos = "above", 
            id_distance = 700, 
            data = dat)
```

