---
title: "20_4stations_2021"
author: "DHJ"
date: "10 3 2021"
output: 
  html_document:
    keep_md: true  
    toc: true  
    toc_float: true
    
---

## 1. Libs  
```{r, warning=FALSE}

shh <- suppressPackageStartupMessages   # ask packages to please be silent when they load

# Check if purrr is installed (we donæt load it because of namespace collision with maps)
if (!"purrr" %in% installed.packages())
  stop(
    "Please install package 'purrr', for instance by running ",
    dQuote("install.packages('purrr')")
  )

shh(library(OpenStreetMap))
shh(library(maps))
shh(library(ggplot2))
shh(library(readxl))
shh(library(dplyr))
shh(library(sf))

shh(library(jsonlite))  # for fromJSON(), used in get_riverlines

shh(library(plotrix)) # for polygon.shadow() (and more?) 
                                                 #   used in floating.pie()

source("20_4stations_2021_functions.R", encoding = "UTF-8")

# Not strictly necessary:
shh(library(mapview))

# CRS strongs for changing projection
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"
crs_utm33 <- "+proj=utm +zone=33 +ellps=WGS84 +datum=WGS84 +units=m"


```


### Save figures
```{r}

save_figures <- TRUE

```


### Define colours for classes  


```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_kort = case_when(
      Status %in% "High" ~ "SG",
      Status %in% "Good" ~ "G",
      Status %in% "Moderate" ~ "M",
      Status %in% "Poor" ~ "D",
      Status %in% "Bad" ~ "SD",
      Status %in% "Unclassified" ~ "NA"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no

```

## 2. Data  
```{r}

fn <- "C:/Data/seksjon 318/Elveovervakning/Data_input/2021/Klassifisering av økologisk tilstand i elver for rapport 2020.xlsx"
# readxl::excel_sheets(fn)

dat <- read_excel(fn, sheet = "Til Dag ") %>%
  mutate(Lat = as.numeric(Lat),
         Long = as.numeric(Long))

n1 <- nrow(dat)

```


### Add colors to data     
One color column for each of the columns Påvekstalger, HBI, Bunndyr

```{r}

dat <- dat %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Påvekst_col = Class_color),
            by = c("Påvekstalger" = "Status_kort")) %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(HBI_col = Class_color),
            by = c("HBI" = "Status_kort")) %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Bunndyr_col = Class_color),
            by = c("Bunndyr" = "Status_kort")) %>%
  left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Combined_col = Class_color),
            by = c("Samlet" = "Status_kort"))  

n2 <- nrow(dat)

if (n1 != n2)
  stop("Error! number of lines changed!")

```


### Interactive map   
* Only for info  
```{r}

# For easxy plotting in mapvio 
# For easxy plotting in mapvio 
datsf_longlat <- sf::st_as_sf(
  dat,
  coords = c("Long", "Lat"), 
  crs = crs_longlat, 
  agr = "constant")  

# Transform to UTM
datsf <- st_transform(datsf_longlat, crs_utm)  

# Transform to Web mercator
datsf_wm <- st_transform(datsf_longlat, 3857)  

mapview(datsf_longlat, zcol = "Elv")

```



## 3. Openstreetmap {.tabset}


### Moelva  

```{r, warning = FALSE}

if (save_figures){
  
  png("Figures/2021/20_4stations_2021_Moelva.png", 
      width = 5, height = 5, units = "in", res = 400)
  plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "left"),
            id_distance = c(250, 250, -500), 
            data = dat,
            maptype = "osm")
  dev.off()

  
}

plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "left"),
            id_distance = c(250, 250, -500), 
            data = dat,
            maptype = "osm")

```

### Brumunda    

```{r, warning = FALSE}

if (save_figures){
  
  png("Figures/2021/20_4stations_2021_Brumunda.png", 
      width = 5, height = 5, units = "in", res = 400)

  plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = c(-500, -500, -1000), 
            data = dat,
            maptype = "osm")

  dev.off()

  
}


plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = -500, 
            data = dat,
            maptype = "osm")

```

### Gausa    

```{r, warning = FALSE}


if (save_figures){
  
  png("Figures/2021/20_4stations_2021_Gausa.png", 
      width = 5, height = 5, units = "in", res = 400)
  
  plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
              id_pos = c("below", "below"),
              id_distance = c(0, 200), 
              data = dat,
              maptype = "osm")
  
  dev.off()

  
}

plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
            id_pos = c("below", "below"),
            id_distance = c(0, 200), 
            data = dat,
            maptype = "osm")

```

### Mesna    

```{r, warning = FALSE}

if (save_figures){
  
  png("Figures/2021/20_4stations_2021_Mesna.png", 
      width = 5, height = 5, units = "in", res = 400)
  
  plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
              id_pos = "above", 
              id_distance = 700, 
              data = dat,
              maptype = "osm")
  
  dev.off()
  
}

plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
            id_pos = "above", 
            id_distance = 700, 
            data = dat,
            maptype = "osm")

```


## 4. ESRI {.tabset}


### Moelva  

```{r, warning = FALSE}

plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "right"),
            id_distance = 250, 
            data = dat,
            maptype = "esri")
```

### Brumunda    

```{r, warning = FALSE}
plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = -500, 
            data = dat,
            maptype = "esri")

```

### Gausa    

```{r, warning = FALSE}
plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
            id_pos = c("below", "below"),
            id_distance = c(0, 200), 
            data = dat,
            maptype = "esri")

```

### Mesna    

```{r, warning = FALSE}

plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
            id_pos = "above", 
            id_distance = 700, 
            data = dat,
            maptype = "esri")
```




## 5. ESRI-topo {.tabset}



### Moelva  

```{r, warning = FALSE}

plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "right"),
            id_distance = 250, 
            data = dat,
            maptype = "esri-topo")
```

### Brumunda    

```{r, warning = FALSE}
plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = -500, 
            data = dat,
            maptype = "esri-topo")

```

### Gausa    

```{r, warning = FALSE}
plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
            id_pos = c("below", "below"),
            id_distance = c(0, 200), 
            data = dat,
            maptype = "esri-topo")

```

### Mesna    

```{r, warning = FALSE}

plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
            id_pos = "above", 
            id_distance = 700,
            data = dat,
            maptype = "esri-topo")

```




## 6. apple-iphoto {.tabset}


### Moelva  

```{r, warning = FALSE}

plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "right"),
            id_distance = 250, 
            data = dat,
            maptype = "apple-iphoto")
```

### Brumunda    

```{r, warning = FALSE}
plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = -500, 
            data = dat,
            maptype = "apple-iphoto")

```

### Gausa    

```{r, warning = FALSE}
plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
            id_pos = c("below", "below"),
            id_distance = c(0, 200), 
            data = dat,
            maptype = "apple-iphoto")

```

### Mesna    

```{r, warning = FALSE}

plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
            id_pos = "above", 
            id_distance = 700, 
            data = dat,
            maptype = "apple-iphoto")
```




## 7. bing {.tabset}


### Moelva  

```{r, warning = FALSE}

plot_river2("Moelva", dlon = 0.10, dlat = 0.05, radius = 300, 
            id_pos = c("left", "right", "right"),
            id_distance = 250, 
            data = dat,
            maptype = "bing")
```

### Brumunda    

```{r, warning = FALSE}
plot_river2("Brumunda", dlon = 0.30, dlat = 0.15, radius = 800, 
            id_pos = c("right", "left", "right"),
            id_distance = -500, 
            data = dat,
            maptype = "bing")

```

### Gausa    

```{r, warning = FALSE}
plot_river2("Gausa", dlon = 0.30, dlat = 0.15, radius = 900, 
            id_pos = c("below", "below"),
            id_distance = c(0, 200), 
            data = dat,
            maptype = "bing")

```

### Mesna    

```{r, warning = FALSE}

plot_river2("Mesna", dlon = 0.10, dlat = 0.05, radius = 350,
            id_pos = "above", 
            id_distance = 700, 
            data = dat,
            maptype = "bing")
```

