---
title: "20_4stations_2021"
author: "DHJ"
date: "10 3 2021"
output: 
  html_document:
    keep_md: true  
    toc: true  
    toc_float: true
    
---

## 1. Libs  
```{r, warning=FALSE}

shh <- suppressPackageStartupMessages   # ask packages to please be silent when they load

# Check if purrr is installed (we donæt load it because of namespace collision with maps)
if (!"purrr" %in% installed.packages())
  stop(
    "Please install package 'purrr', for instance by running ",
    dQuote("install.packages('purrr')")
  )

shh(library(OpenStreetMap))
shh(library(maps))
shh(library(ggplot2))
shh(library(readxl))
shh(library(dplyr))
shh(library(sf))

shh(library(jsonlite))  # for fromJSON(), used in get_riverlines

shh(library(plotrix)) # for polygon.shadow() (and more?) 
                                                 #   used in floating.pie()

source("20_4stations_2021_functions.R", encoding = "UTF-8")

# Not strictly necessary:
shh(library(mapview))

# CRS strongs for changing projection
crs_longlat <- "+proj=longlat +ellps=WGS84 +datum=WGS84"
crs_utm <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m"
crs_utm33 <- "+proj=utm +zone=33 +ellps=WGS84 +datum=WGS84 +units=m"


```


### Save figures
```{r}

# save_figures <- TRUE
save_figures <- FALSE

```


### Define colours for classes  


```{r, fig.width=3.5, fig.height=2.5}

# Order in plots etc.
class_levels <- c("Svært dårlig", "Dårlig", "Moderat", "God", "Svært god", "Uklassifisert")

# Read standard colors
df_colors <- read_excel("Data_input/Fargekoder RGB for tilstandsklassifisering.xlsx", sheet = 2) %>%
  mutate(
    Status_no = case_when(
      Status %in% "High" ~ "Svært god",
      Status %in% "Good" ~ "God",
      Status %in% "Moderate" ~ "Moderat",
      Status %in% "Poor" ~ "Dårlig",
      Status %in% "Bad" ~ "Svært dårlig",
      Status %in% "Unclassified" ~ "Uklassifisert"),
    Status_kort = case_when(
      Status %in% "High" ~ "SG",
      Status %in% "Good" ~ "G",
      Status %in% "Moderate" ~ "M",
      Status %in% "Poor" ~ "D",
      Status %in% "Bad" ~ "SD",
      Status %in% "Unclassified" ~ "NA"),
    Status_no = factor(Status_no, levels = class_levels),
    Class_color = rgb(R/255, G/255, B/255)
  ) %>%
  arrange(Status_no)
df_colors


# Show colors
par(mar = c(0,0,2,0))
pie(rep(1,6), 
    col = df_colors$Class_color, 
    labels = df_colors$Status_no, 
    main = "Colors for nEQr classes")  

# Also make named list
class_colors <- df_colors$Class_color
names(class_colors) <- df_colors$Status_no


```

### For the legend    
Copy-pasted to Powerpoint file and modified there  
```{r, fig.width=3, fig.height=3}

# Using a modified version of pie() where 'lwd' (line width) works
pie(rep(1,3), col = "white", label = "", lwd = 2)  

gg <- df_colors %>%
  mutate(X = 1,
         Status_no = forcats::fct_rev(Status_no)) %>%
  ggplot(aes(x = Status_no, y = X, fill = Status_no)) +
  geom_col() +
  scale_fill_manual(values = rev(df_colors$Class_color)) 

cowplot::plot_grid(
  cowplot::get_legend(gg)
  )
  

```


## 2. Data    

### Raw data
```{r}

# 2021
fn <- "C:/Data/seksjon 318/Elveovervakning/Data_input/2021/Klassifisering av økologisk tilstand i elver for rapport 2020.xlsx"

# 2022
fn <- "C:/Data/seksjon 318/Elveovervakning/Data_input/2022/Vanntyper og punching av indeksverdier  (1).xlsx"
# readxl::excel_sheets(fn)

dat <- read_excel(fn) %>%
  mutate(Lat = as.numeric(`Breddegrad, nord`),
         Long = as.numeric(`Lengdegrad, øst`))

n1 <- nrow(dat)

# Column names hard-coded in functions
dat <- dat %>%
  rename(`Vannforekomst ID` = `Vann-forekomst-ID`)


# For this purpose, we use "Samlet" for the quality of the entire Vannforekomst (not on station level)
# So we set it to "God" for Mesna (following mean of nEQR, not shown here)

# 2022: SKIP THIS SO FAR

# dat <- dat %>%
#   mutate(Samlet = case_when(
#     Elv == "Mesna" ~ "G",
#     TRUE ~ Samlet
#   ))

```

```{r}
# > str(dat)
# tibble [12 x 11] (S3: tbl_df/tbl/data.frame)
#  $ Elv             : chr [1:12] "Brumunda" "Brumunda" "Brumunda" "Moelva" ...
#  $ Stasjonsnavn    : chr [1:12] "Brumunda, nær utløpet i Mjøsa" "Lera ,ved Lera bru" "Brumunda, nedstrøms Brumund sag" ...
#  $ Lat             : num [1:12] 60.9 60.9 61 60.9 60.9 ...
#  $ Long            : num [1:12] 10.9 11 11 10.7 10.8 ...
#  $ Vannforekomst   : chr [1:12] "Brumunda, nedre del" "Lera" "Brumunda Ljøsåa - Lera" "Moelva nedstrøms Strand Unikorn" ...
#  $ Vannforekomst ID: chr [1:12] "002-335-R" "002-620-R" "002-4841-R" "002-2590-R" ...
#  $ Påvekstalger    : chr [1:12] "M" "G" "G" "G" ...
#  $ HBI             : chr [1:12] "SG" "SG" "SG" "G" ...
#  $ Bunndyr         : chr [1:12] "M" "SG" "SG" "SG" ...
#  $ Tot-P           : chr [1:12] "NA" "NA" "NA" "NA" ...
#  $ Samlet          : chr [1:12] "M" "G" "G" "G" ...

```



### Add colors to data     
One color column for each of the columns Påvekstalger, HBI, Bunndyr
* Note:  
    - PIT = index for Påvekstalger (see Veileder 02-2018 page 20)
    - HBI = index for Heterotrof begroing (see Veileder 02-2018 page 60)      
    - ASPT = index for Bunndyr   
```{r}

# 2021 version - status given as SG, G, M
# dat <- dat %>%
#   left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Påvekst_col = Class_color),
#             by = c("Tilstand PIT" = "Status_kort")) %>%
#   left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(HBI_col = Class_color),
#             by = c("Tilstand HBI2" = "Status_kort")) %>%
#   left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Bunndyr_col = Class_color),
#             by = c("Bunndyr" = "Status_kort")) %>%
#   left_join(df_colors %>% select(Status_kort, Class_color) %>% rename(Combined_col = Class_color),
#             by = c("Samlet" = "Status_kort"))  

# 2022 version - status given as Svært god, God, Moderat
dat <- dat %>%
  left_join(df_colors %>% select(Status_no, Class_color) %>% rename(Påvekst_col = Class_color),
            by = c("Tilstand PIT" = "Status_no")) %>%
  left_join(df_colors %>% select(Status_no, Class_color) %>% rename(HBI_col = Class_color),
            by = c("Tilstand HBI2" = "Status_no")) %>%
  left_join(df_colors %>% select(Status_no, Class_color) %>% rename(Bunndyr_col = Class_color),
            by = c("Tilstand ASPT" = "Status_no"))
n2 <- nrow(dat)

if (n1 != n2)
  stop("Error! number of lines changed!")

# Remove empty lines at the end  
dat <- dat %>%
  filter(!is.na(Lat))

```


### Check that we have what we need    

* Note that this year (in contrast to 2021) we just set a fixed color for the river  
    - Thus we don't need `Combined_col`  

```{r}

#
# NOTE: check what you need 
#

# Obligatory variables IF river should be colored using 'Combined_col'
vars <- c("Elv", "Vannforekomst ID", "Long", "Lat" ,
          "Påvekst_col", "HBI_col", "Bunndyr_col", "Combined_col") # INCLUDE Combined_col

# Obligatory variables IF river will be given just a constant color
vars <- c("Elv", "Vannforekomst ID", "Long", "Lat" ,
          "Påvekst_col", "HBI_col", "Bunndyr_col")   # NO Combined_col

check <- !vars %in% names(dat)
# check <- vars %in% names(dat)

if (sum(check) > 0){
  stop("Lacking variables: ", paste(vars[check], collapse = ", "), "!\n",
       "This/these variables are needed for 'plot_river2'")
} else {
  message("Variables checked")
}

```



### Interactive map   
* Only for info  
```{r}

dat

vars <- c("Elv", "Elvestrekning", "Vannforekomst ID", "Steds-beskrivelse", 
          "Vanntype", "Aquamonitor kode", "Stasjons kode (bunndyr)", 
          "Stasjonskode (Begroingsalger)", "Tilstand PIT", "Tilstand AIP", "Tilstand HBI2", "Lat", "Long", 
          "Påvekst_col", "HBI_col", "Bunndyr_col")

# For easy plotting in mapview 
datsf_longlat <- sf::st_as_sf(
  dat[vars],
  coords = c("Long", "Lat"), 
  crs = crs_longlat, 
  agr = "constant")  

# Transform to UTM
datsf <- st_transform(datsf_longlat, crs_utm)  

# Transform to Web mercator
datsf_wm <- st_transform(datsf_longlat, 3857)  

mapviewOptions(fgb = FALSE)       # probably needed
mapview(datsf_longlat, zcol = "Elv")


```




## 3. Openstreetmap {.tabset}

* Note that this year (in contrast to 2021) we just set a fixed color
`river_col = "deepskyblue"` for the river, instaed of coloring according to status  


### Hunnselva  

```{r, warning = FALSE}

# dir.create("Figures/2022")

rivername <- "Hunnselva"

if (save_figures){
  png(paste0("Figures/2022/20_4stations_2022_", rivername, ".png"), 
      width = 5, height = 5, units = "in", res = 400)
}

# debugonce(plot_river2)
plot_river2(rivername, river_col = "deepskyblue",
            dlon = 0.40, dlat = 0.20, radius = 1200, 
            id_pos = c("left", "right", "left"),
            id_distance = c(1500, 1500, 1500), 
            data = dat,
            maptype = "osm")

if (save_figures){
  dev.off()
}

```

### Lågen  

```{r, warning = FALSE}


rivername <- "Lågen"

if (save_figures){
  png(paste0("Figures/2022/20_4stations_2022_", rivername, ".png"), 
      width = 5, height = 5, units = "in", res = 400)
}

# debugonce(plot_river2)
plot_river2(rivername, river_col = "deepskyblue1", 
            dlon = 0.40, dlat = 0.20, radius = 1200, 
            id_pos = c("left", "right", "left"),
            id_distance = c(1000, 0, 200), 
            data = dat,
            maptype = "osm")

if (save_figures){
  dev.off()
}

```

### Svartelva  
* Note: three sampling points, but ony two vannforekomst  
```{r, warning = FALSE}


rivername <- "Svartelva"

if (save_figures){
  png(paste0("Figures/2022/20_4stations_2022_", rivername, ".png"), 
      width = 5, height = 5, units = "in", res = 400)
}



# debugonce(plot_river2)
plot_river2(rivername, river_col = "deepskyblue", 
            dlon = 0.40, dlat = 0.20, radius = 1200, 
            id_pos = c("below", "right"),
            id_distance = c(300, -1900), 
            data = dat,
            maptype = "osm")

if (save_figures){
  dev.off()
}

```


### Vikselva  
* Note: three sampling points, but ony two vannforekomst  
```{r, warning = FALSE}


rivername <- "Vikselva"

if (save_figures){
  png(paste0("Figures/2022/20_4stations_2022_", rivername, ".png"), 
      width = 5, height = 5, units = "in", res = 400)
}


# debugonce(plot_river2)
plot_river2(rivername, river_col = "deepskyblue", 
            dlon = 0.26, dlat = 0.13, radius = 600, 
            id_pos = c("above", "left"),
            id_distance = c(1500, -3000), 
            data = dat,
            maptype = "osm")

if (save_figures){
  dev.off()
}

```
## 4. Copy to K  
```{r}

if (FALSE){
  
  fns <- dir("Figures/2022", full.names = TRUE)
  
  for (fn in fns)
    file.copy(fn, "K:/Avdeling/214-Oseanografi/DHJ/Prosjekter/Mjøsa_2021")
  
}


```

